---
title: "DAG"
author: "Shadi"
date: "2023-06-20"
output:
  pdf_document:
    keep_tex: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
---


```{r wd-setup, include=FALSE}

wd <- list()
# commonly used paths in my working directory
wd$data   <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/data/"
wd$output <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/output/"
wd$texts <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/texts"
wd$codes <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/codes/R/"

```


```{r setup , include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.align = "center",
                      fig.width = 4, 
                      fig.height = 4, 
                      fig.path = wd$output,
                      dev = "png",
                      dpi = 200,
                      warning=FALSE
                      )


```



<!-- message=FALSE and/or warning=FALSE -->

```{r library ,  include=FALSE}

library(dplyr)  # This will also load the magrittr package
library(pcalg)
library(dagitty)
library(ggdag)
library(ggplot2)
library(graph)
library(brew)
library(BiocGenerics)

```

```{r data}
load(paste0(wd$data,"Data.Rdata"))
Forgn<- Data[Data$NATIVITY == "Foregin-born", ]
NATV<- Data[Data$NATIVITY == "US-born", ]

data1 <- subset(Data, select = c(IPC,ENG,LTINU,CORIGIN, SEX,DIS,AGEP, SCHLG, MARG, ESRG, RACE1,POVPIP,treat,UnempR,ADA,CIT,HINS4))
data2 <- subset(Forgn, select = c(IPC,ENG,LTINU,CORIGIN, SEX,DIS,AGEP, SCHLG, MARG, ESRG, RACE1,POVPIP,treat,UnempR,ADA,CIT,HINS4))
data3 <- subset(Data, select = c(IPC,ENG,LTINU,CORIGIN, SEX,DIS,AGEP, SCHLG, MARG, ESRG, RACE1,POVPIP,treat,UnempR,ADA,CIT,UNINS))
data4 <- subset(Forgn, select = c(IPC,ENG,LTINU,CORIGIN, SEX,DIS,AGEP, SCHLG, MARG, ESRG, RACE1,POVPIP,treat,UnempR,ADA,CIT,UNINS))

variables = colnames(data1)
variables[3] <- "ACUL" 
variables[7] <- "AGE" 
variables[8] <- "EDUC" 
variables[9] <- "EMPLY" 
variables[10] <- "RACE"
variables[11] <- "POV" 
variables[17] <- "INSURED" 



colnames(data1) = c(1:ncol(data1))
# Create an empty list to store the matrices

```

### Causal Structure Discovery

I utilized causal structure discovery techniques to accurately represent
the data generating process and unveil the underlying causal
relationships among the variables. The causal structure discovery
approach identifies potential causal relationships based on patterns and
dependencies observed in the data. The resulting Directed Acyclic Graph
(DAG) from the causal discovery is capturing the complex interplay
between the variables, accounting for confounding factors and potential
biases, and providing credible evidence for the causal effects of
medicaid expansion on medicaid take-up and uninsured rate.

By utilizing the DAG obtained through the causal discovery approach, I
can conduct backdoor and front door analyses, enabling the
identification of the minimal adjustment set. The minimal adjustment set
represents the smallest subset of variables that must be controled for
to obtain unbiased estimates of causal effects.

In the initial phase of our analysis, a DAG , as shown in Graph 1, was
generated using multiple constraint-based and score-based algorithms
including GDS algorithms, Greedy Equivalence Search (GES), Peter-Clark
(PC) algorithm, and Fast Causal Inferences (FCI). To integrate the
information obtained from these algorithms, following Joe et al.(2023) I
employed a majority voting approach. This involved considering each edge
and determining its presence in the final graph based on whether it
appeared in more than 50% of the cases, indicating agreement among the
majority of the algorithms.

```{r DAG1}


####################
## Identify Causal Graph
####################


matMajVotingList <- list()

# Loop through data1 to data4
for (i in 1:4) {
        # Get the current data
        currentData <- get(paste0("data", i))
        
        # Convert character variables to factors
        currentData <- currentData %>% mutate_if(is.character, as.factor)
        
        # Convert factor variables to numeric
        currentData <- currentData %>% mutate_if(is.factor, as.numeric)
        
        # 1.Perform the GES algorithm
        score <- new("GaussL0penObsScore", currentData)
        ges1.fit <- ges(score, fixedGaps = NULL, adaptive = "vstructures", phase = "forward", maxDegree = integer(0), verbose = FALSE)
        
        # Create the matrix for GES algorithm
        p <- dim(currentData)[2]
        matGES <- matrix(0, nrow = p, ncol = p)
        row <- 1
        for (list in ges1.fit$essgraph$.in.edges) {
                for (node in list) {
                        matGES[node, row] <- 1
                }
                row <- row + 1
        }
        
        # 2. Perform the GDS algorithm
        gds.fit <- gds(score, fixedGaps = NULL, adaptive = "triples", phase = "forward", maxDegree = integer(0), verbose = FALSE)
        
        # Create the matrix for GDS algorithm
        matGDS <- matrix(0, nrow = p, ncol = p)
        row <- 1
        for (list in gds.fit$essgraph$.in.edges) {
                for (node in list) {
                        matGDS[node, row] <- 1
                }
                row <- row + 1
        }
        
        # 3. Perform the PC algorithm
        SuffStat <- list(C = cor(currentData), n = nrow(currentData))
        result.pc <- pc(suffStat = SuffStat, indepTest = gaussCItest, labels = colnames(currentData), alpha = 0.01)
        
        # Create the matrix for PC algorithm
        matPC <- matrix(0, nrow = p, ncol = p)
        row <- 1
        for (list in result.pc@graph@edgeL) {
                for (node in list) {
                        matPC[node, row] <- 1
                }
                row <- row + 1
        }
        
        # 4.Perform the RFCI algorithm
        result.rfci <- rfci(SuffStat, indepTest = gaussCItest, p = ncol(currentData), alpha = 0.01)
        
        # Create the matrix for RFCI algorithm
        matRFCI <- matrix(0, nrow = p, ncol = p)
        item <- 0
        for (l in result.rfci@amat) {
                row <- item %% p + 1
                column <- as.integer(item / p) + 1
                if (l == 2)
                        matRFCI[row, column] <- 1
                if (l == 3)
                        matRFCI[column, row] <- 1
                item <- item + 1
        }
        
        # Majority voting of the DAG
        matMajVoting <- matGES + matGDS + matPC + matRFCI
        
        # Store the matrix in the list
        matMajVotingList[[i]] <- matMajVoting
}

# Access the matrices from the list
matMajVoting1 <- matMajVotingList[[1]]
matMajVoting2 <- matMajVotingList[[2]]
matMajVoting3 <- matMajVotingList[[3]]
matMajVoting4 <- matMajVotingList[[4]]

MajVoting <- matMajVoting1 + matMajVoting2 + matMajVoting3 + matMajVoting4

#MajVotingF <- matMajVoting2 + matMajVoting4

# create a DAG based on majority voting 

digraph <- "dag {"  # Initialize the digraph as an empty string

for(i in 1:p){
        for(j in 1:p){
                if(MajVoting[i, j] > 8){ # change the value 2 to an appropriate value (threshold)
                        #print(variables[i])
                        digraph <- paste0(digraph, variables[i], "->", variables[j],";")
                }
        }
}

digraph <- gsub(";$", "}", digraph) # change the last ; to } to make it compatible for Dagitty function 

# create DAG object
dag <- dagitty(digraph)
exposures(dag) <- "treat"
outcomes(dag) <- "INSURED"

# DAG representation
# 
# 
# 
 DAG1<-tidy_dagitty(dag, layout = "grid") %>% 
     ggdag_status(edge_type="link_arc",text_size=2.7,node_size=20, check_overlap = TRUE)+guides(color = FALSE) + 
     theme_dag_blank()
 
    DAG1$layers[[3]]$mapping <- aes(colour = status)
    DAG1 + scale_color_manual(na.value ="#222D5a" , values = c(exposure ="#A94064" , outcome = "#44AA99")) +
            scale_fill_manual(na.value ="#222D5a", values = c(exposure ="#A94064" , outcome = "#44AA99"))


 
```

### Revised casual graph

To enhance the accuracy of the causal relationships represented in the
DAG, I carefully reviewed and manually edited the graph by removing
paths that contradicted my domain knowledge or appeared implausible
within the context. By applying these revisions, the resulting DAG,
illustrated in graph 2, aligns more closely with my expertise in the
field and provides a more trustworthy representation of the underlying
causal structure in my analysis.

```{r DAG2, echo=FALSE}
findag<-dagitty('dag{
 bb="-5.958,-4.932,7.16,5.438"
 "Life Lived in US" [pos="-2.079,1.854"]
 "State Political Ideology" [pos="-4.930,0.020"]
 "Age" [pos="1.789,-1.856"]
 "Citizenship Status" [pos="-2.079,2.842"]
 "Disability" [pos="1.789,-2.675"]
 "English Proficiency" [pos="-2.079,3.801"]
 "Employment" [pos="-2.079,-3.112"]
 "Immigration Policy Climate" [pos="-4.554,2.786"]
 "Marital Status" [pos="1.811,-1.080"]
 "Income-to-Poverty Ratio" [pos="-2.068,-0.657"]
 "Race/Ethnicity" [pos="1.789,-0.107"]
 "Cultural Grouping" [pos="-2.090,4.930"]
 "Education" [pos="-2.046,-2.068"]
 "Sex" [pos="1.800,-3.676"]
 "Medicaid Take-Up" [outcome,pos="1.822,1.304"]
 "Unemployment Rate" [pos="-3.858,0.006"]
 "Medicaid Expansion" [exposure,pos="-4.389,1.276"]
 "Life Lived in US" -> "English Proficiency"
 "State Political Ideology" -> "Immigration Policy Climate"
 "State Political Ideology" -> "Unemployment Rate"
 "State Political Ideology" -> "Medicaid Expansion"
 "Age" -> "Life Lived in US"
 "Age" -> "Disability"
 "Age" -> "Employment"
 "Age" -> "Medicaid Take-Up"
 "Citizenship Status" -> "State Political Ideology"
 "Citizenship Status" -> "English Proficiency"
 "Citizenship Status" -> "Marital Status"
 "Citizenship Status" -> "Income-to-Poverty Ratio"
 "Citizenship Status" -> "Education" 
 "Citizenship Status" -> "Medicaid Take-Up"
 "Citizenship Status" -> "Employment"
 "Disability" -> "Employment"
 "Disability" -> "Education" 
 "Disability" -> "Medicaid Take-Up"
 "English Proficiency" -> "Employment"
 "English Proficiency" -> "Medicaid Take-Up"
 "Employment" -> "Income-to-Poverty Ratio"
 "Employment" -> "Medicaid Take-Up"
 "Immigration Policy Climate"  -> "Income-to-Poverty Ratio"
 "Immigration Policy Climate"  -> "Medicaid Take-Up"
 "Marital Status" -> "Income-to-Poverty Ratio"
 "Marital Status" -> "Medicaid Take-Up"
 "Income-to-Poverty Ratio" -> "Medicaid Take-Up"
 "Race/Ethnicity" -> "Education"  
 "Cultural Grouping" -> "English Proficiency"
 "Cultural Grouping" -> "Employment"
 "Cultural Grouping" -> "Race/Ethnicity"
 "Cultural Grouping" -> "Education" 
 "Cultural Grouping" -> "Medicaid Take-Up"
 "Education" -> "English Proficiency"
 "Education" -> "Employment"
 "Education" -> "Medicaid Take-Up"
 "Sex" -> "Employment"
 "Sex" -> "Medicaid Take-Up"
 "Unemployment Rate" -> "Employment"
 "Unemployment Rate" -> "Education"
 "Unemployment Rate" -> "Medicaid Take-Up"
 "Unemployment Rate" -> "Medicaid Expansion"
 "Medicaid Expansion" -> "Medicaid Take-Up"
}')

FINDAG <- ggdag_status(findag, node_size = 10, use_labels = "name", text_size = 3, label_size = 6, text = FALSE) +
  guides(color = "none") +  # Turn off legend
  theme_dag() 


FINDAG$layers[[3]]$mapping <- aes(colour = status)
FINDAG + scale_color_manual(na.value ="#222D5a" , values = c(exposure ="#A94064" , outcome = "#44AA99")) +
        scale_fill_manual(na.value ="#222D5a", values = c(exposure ="#A94064" , outcome = "#44AA99"))


```

### Minimal adjustment set

The identified causal relationship between Medicaid expansion and
Medicaid take-up in the revised DAG provides compelling evidence that
changes in the treatment variable directly influence changes in the
outcome variable. This finding suggests that interventions targeting the
treatment variable, such as expanding Medicaid coverage, can potentially
have a substantial impact on improving the rate of Medicaid take-up.

by conducting backdoor analysis I identified the necessary adjustment
set, revealing that variables Citizenship Status, Immigration Policy
Climate, Unemployment Rate need to be controlled for to accurately
estimate the causal effect between Medicaid expansion and Medicaid
take-up.

```{r DAG2Adj, echo=TRUE}
adjustmentSets(findag)

```

### Simplified causal graph

To enhance the clarity and interpretability of the graph, I employed a
strategy to simplify its complexity. This involved grouping related
variables into single nodes, such as combining 'education,' 'income,'
and 'employment' into a unified node labeled 'Socioeconomic.' The
streamlined representation of the underlying relationships can be
observed in Graph 3.

```{r DAG3, echo=FALSE}


shaddag<-dagitty('dag {
        bb="-3.828,-4.241,3.728,3.459"
        "State Political Ideology" [pos="-3.274,-2.020"]
         Demographics [pos="0.049,-1.978"]
        "Medicaid Expansion" [exposure,pos="-2.803,-0.805"]
        "Immigration Policy Climate" [pos="-2.771,0.180"]
        "Foregin-Born" [pos="-1.294,0.128"]
        "Socioeconomic" [pos="-1.288,-2.010"]
        "Medicaid Take-Up" [outcome,pos="0.049,-0.763"]
        "Unemployment Rate" [pos="-2.478,-2.020"]
        "State Political Ideology" -> "Medicaid Expansion"
        "State Political Ideology" -> "Immigration Policy Climate"
        "State Political Ideology" -> "Unemployment Rate"
        "State Political Ideology" -> "Medicaid Take-Up"
        Demographics -> "Socioeconomic"
        Demographics -> "Medicaid Take-Up"
        "Medicaid Expansion" -> "Medicaid Take-Up"
        "Immigration Policy Climate" -> "Foregin-Born"
        "Immigration Policy Climate" -> "Medicaid Take-Up"
        "Foregin-Born" -> "Socioeconomic"
        "Foregin-Born" <-> "Demographics"
        "Foregin-Born" -> "Medicaid Take-Up"
        "Socioeconomic" -> "Medicaid Take-Up"
        "Unemployment Rate" -> "Medicaid Expansion"
        "Unemployment Rate" -> "Immigration Policy Climate"
        "Unemployment Rate" -> "Socioeconomic"
        "Unemployment Rate" -> "Medicaid Take-Up"
}')

## Create simplified  DAG

DAGSHADI<-ggdag_status(shaddag,node_size = 10,use_labels = "name", text = FALSE)+
        guides(color = FALSE) +  # Turn off legend
        theme_dag()

DAGSHADI$layers[[3]]$mapping <- aes(colour = status)
DAGSHADI + scale_color_manual(na.value ="#222D5a" , values = c(exposure ="#A94064" , outcome = "#44AA99")) +
        scale_fill_manual(na.value ="#222D5a", values = c( exposure ="#A94064" , outcome = "#44AA99")) # other coloer = "#ffc300",  


```

Although utilizing causal discovery algorithms has limitations, such as
assuming the adequacy of observed variables and relying on the absence
of unobserved confounders, efforts were made to include relevant
variables in the analysis. However, it is possible that unmeasured
confounders may exist, potentially introducing biases into the
identified causal relationships. Therefore, the obtained graph may not
precisely represent the true underlying causal structure..

Due to these limitations, I do not solely rely on this graph and its
suggested adjustment set for estimating causal effects in my analysis.
Nonetheless, the DAG derived from the causal discovery approach serves
as a valuable tool for generating hypotheses and guiding the modeling
process, as well as informing the selection of control variables in my
DID approach analysis.
