---
title: "Descriptive"
author: "Shadi"
date: "2023-06-20"
output:
  html_document:
    df_print: paged
---


```{r wd-setup, include=FALSE}

wd <- list()
# commonly used paths in my working directory
wd$data   <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/data/"
wd$output <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/output/"
wd$texts <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/texts"
wd$codes <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/codes/R/"

```


```{r data, include=FALSE}

load(paste0(wd$data,"Data.Rdata"))
Forgn<- Data[Data$NATIVITY == "Foregin-born", ]
NATV<- Data[Data$NATIVITY == "US-born", ]

```


```{r chunk-setup , include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.align = "center",
                      fig.width = 4, 
                      fig.height = 4, 
                      fig.path = wd$output,
                      dev = "png",
                      cache = TRUE,
                      warning=FALSE,
                      message=FALSE

                      )
```


```{r library ,  include=FALSE}

library(tidyverse)
library(gtsummary)
library(survey)
library(gt)

```

```{r svydesign}
svy <- svydesign(
                  id=~1,
                  weights = ~ PWGTP, 
                  repweights = ~ matches("PWGTP[0-9]+"), 
                  data = Data, 
                  type = "JK1",
                  scale = 4/80,
                  rscales = rep(1, 80),
                  mse = TRUE
            )
```

### Table 1: Baseline Characteristics for states

```{r table-1 }

t1<-Data %>% 
        filter(ACA=="Pre-ACA")%>%
        select(ADA,IPC, UnempR,expansion) %>%
            tbl_summary(
                    by = expansion,
                    label = list(ADA ~ "State's Political Liberalism",
                                 UnempR ~"State's Unemployment Rate",
                                 IPC ~ "Immigration Policy Climate"
                                  ),
                     statistic = list(all_continuous() ~ "{mean} ({sd})")
                     )%>%
                      add_difference() %>%
                      add_significance_stars(hide_ci = TRUE, hide_p = FALSE)%>%
                      modify_caption("**Table 1. Baseline Comparison of States**") %>%
                     # modify_spanning_header(all_stat_cols() ~ "**Table 1.Baseline Comparison of States**") %>%
                      modify_header(
                                  label = "**Variable**",
                                  stat_1 = '**Non Expansion**',
                                   stat_2 = '**Expansion**'
                             )
# tab1 # check if all is correct

# create post-aca table for states variable

t2<-Data %>% 
  filter(ACA=="Post-ACA")%>%
  select(ADA,IPC, UnempR,expansion) %>%
  tbl_summary(
    by = expansion,
    label = list(ADA ~ "State's Political Liberalism",
                 UnempR ~"State's Unemployment Rate",
                 IPC ~ "Immigration Policy Climate"
    ),
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  )%>%
  add_difference() %>%
  add_significance_stars(hide_ci = TRUE, hide_p = FALSE)%>%
  modify_caption("**Table 1. Baseline Comparison of States**") %>%
  # modify_spanning_header(all_stat_cols() ~ "**Table 1.Baseline Comparison of States**") %>%
  modify_header(
    label = "**Variable**",
    stat_1 = '**Non Expansion**',
    stat_2 = '**Expansion**'
  )


#tab2 # check if everything is correct

## Stack two tables to create table 1

table1 <-
  tbl_stack(list(t1, t2), group_header = c("**Pre-ACA**", "**Post-ACA**"))

 as_gt(table1) %>% gt::as_latex()


```

### Table 2: Baseline Characteristics by Nativity


```{r table-2 }

table2<-svy %>% subset(ACA=="Pre-ACA")%>%
      tbl_strata(
           strata = expansion,
          .tbl_fun = ~ .x %>% 
                tbl_svysummary(
                         by = NATIVITY,
                         include = c(
                                 UNINS, HINS4, AGEP, SEX,  DIS, 
                                 ESRG, MARG ,SCHLG , RACE1,POVPIPG,
                                 CIT,LTINU,ENG,CULRG,CORIGIN 
                                     ),
                         missing = "no",
                         label = list(
                               AGEP ~ "Age", UNINS ~ "Uninsured",
                               HINS4 ~ "Medicaid coverage", SEX ~ "Sex", DIS ~"Disability",
                               ESRG~"Current employment status", MARG ~"Marital status",
                               SCHLG~"Education" , RACE1~"Race/ethnicity",POVPIPG ~ "Federal poverty",
                               CIT~"Citizenship status",LTINU ~"Lifetime in US",
                               ENG~"Self-rated English proficiency", 
                               CORIGIN~"Country/Region of birth", CULRG~"Cultural clusters"
                                     )
                              ) %>%
                add_p()                  %>%
                  #add_p (
                  # perform t-test for all variables
                  #test = list(all_continuous() ~ "t.test", all_categorical() ~ "chisq.test"),
                  # assume equal variance in the t-test
                  # test.args = all_tests("t.test") ~ list(var.equal = TRUE)
                        #)                 %>%
               add_significance_stars(hide_ci = TRUE, hide_p = FALSE)%>%
               italicize_labels() %>%
               bold_labels() %>%
               modify_caption("**Table 2.Baseline Characteristics by Nativity**")
              #modify_spanning_header(stat_1 ~ "**Non Expansion**", stat_2 ~ "**Expansion**")
            )
  
  table2
  
  
```

### Table 3: Uninsured rate before and after ACA for expansion and non-expansion state by characteristics
```{r table-3}

t1<- Data %>% 
      filter(expansion=="expansion")%>%
      select(UNINS, CIT, LTINU,  RACE1, SEX,ESRG, MARG, SCHLG,POVPIPG, ENG,CULRG, CORIGIN, DIS,expansion,ACA) %>%  
      tbl_strata(
           strata = ACA,
          .tbl_fun = ~ .x %>%  
                  tbl_summary(
                        by = UNINS,
                        include = c(CIT, LTINU,  RACE1,SEX,ESRG, MARG, SCHLG,POVPIPG, ENG, CORIGIN, DIS,CULRG) ,
                        label = list(
                                     RACE1~"Race/ethnicity", CIT~"Citizenship status",LTINU ~"Lifetime in US",
                                     SEX ~ "Sex", DIS ~"Disability", ESRG~"Current employment status", MARG ~"Marital status",
                                     SCHLG~"Education" , POVPIPG ~ "Federal poverty",ENG~"Self-rated English proficiency",
                                     CORIGIN~"Country/Region of birth", CULRG~"Cultural clusters"
                                     ), 
                        percent = "row",
                        statistic = list(all_categorical() ~ "{p}%")
                             ) %>%
                    modify_column_hide(columns = stat_1)%>%
                    italicize_labels() #%>%
                    # modify_header(stat_2 = "N = {n} ({style_percent(p)}%)") %>%
                    # modify_footnote(update = everything() ~ NA) # if you'd like no footnote remove #
                )

 t2<- Data %>% 
   filter(expansion=="Non-expansion")%>%
   select(UNINS, CIT, LTINU,  RACE1, SEX,ESRG, MARG, SCHLG,POVPIPG, ENG,CULRG, CORIGIN, DIS,expansion,ACA) %>%  
   tbl_strata(
       strata = ACA,
      .tbl_fun = ~ .x %>%  
           tbl_summary(
                      by = UNINS,
                      include = c(CIT, LTINU,  RACE1,SEX,ESRG, MARG, SCHLG,POVPIPG, ENG, CORIGIN, DIS,CULRG) ,
                      label = list (
                                RACE1~"Race/ethnicity", CIT~"Citizenship status",LTINU ~"Lifetime in US",
                                SEX ~ "Sex", DIS ~"Disability", ESRG~"Current employment status", MARG ~"Marital status",
                                SCHLG~"Education" , POVPIPG ~ "Federal poverty",ENG~"Self-rated English proficiency",
                                CORIGIN~"Country/Region of birth", CULRG~"Cultural clusters"
                                   ), 
                      percent = "row",
                      statistic = list(all_categorical() ~ "{p}%")
                     ) %>%
          modify_column_hide(columns = stat_1) %>%
          italicize_labels() #%>
            )
 
# creating the merged table out of the t1 and t2
 table3<-tbl_merge(
              tbls = list(t1, t2),
              tab_spanner = c("**Expansion**", "**Non-expansion**")
                 )%>%
               modify_header(
                 stat_2_1_1 = "**Pre-ACA** ({style_percent(p)}%)",
                 stat_2_2_1 = "**Post-ACA** ({style_percent(p)}%)",
                 stat_2_1_2 = "**Pre-ACA** ({style_percent(p)}%)",
                 stat_2_2_2 = "**Post-ACA** ({style_percent(p)}%)"
                 ) %>%
               modify_caption("**Table 3.Uninsured rate before and after ACA for expansion and non-expansion by characteristics**")

 
table3

 as_gt(table3) 

```


### Table 4: Medicaid coverage rate before and after ACA for expansion and non-expansion state by characteristics

```{r table-4}
 
t1<- Data %>% 
   filter(expansion=="expansion")%>%
   select(HINS4, CIT, LTINU,  RACE1, SEX,ESRG, MARG, SCHLG,POVPIPG, ENG,CULRG, CORIGIN, DIS,expansion,ACA) %>%  
   tbl_strata(
     strata = ACA,
     .tbl_fun = ~ .x %>%  
       tbl_summary(
         by = HINS4,
         include = c(CIT, LTINU,  RACE1,SEX,ESRG, MARG, SCHLG,POVPIPG, ENG, CORIGIN, DIS,CULRG) ,
         label = list(
           RACE1~"Race/ethnicity", CIT~"Citizenship status",LTINU ~"Lifetime in US",
           SEX ~ "Sex", DIS ~"Disability", ESRG~"Current employment status", MARG ~"Marital status",
           SCHLG~"Education" , POVPIPG ~ "Federal poverty",ENG~"Self-rated English proficiency",
           CORIGIN~"Country/Region of birth", CULRG~"Cultural clusters"
         ), 
         percent = "row",
         statistic = list(all_categorical() ~ "{p}%")
       ) %>%
       modify_column_hide(columns = stat_1)%>%
       italicize_labels() #%>%
     # modify_header(stat_2 = "N = {n} ({style_percent(p)}%)") %>%
     # modify_footnote(update = everything() ~ NA) # if you'd like no footnote remove #
   )
 
 t2<- Data %>% 
   filter(expansion=="Non-expansion")%>%
   select(HINS4, CIT, LTINU,  RACE1, SEX,ESRG, MARG, SCHLG,POVPIPG, ENG,CULRG, CORIGIN, DIS,expansion,ACA) %>%  
   tbl_strata(
     strata = ACA,
     .tbl_fun = ~ .x %>%  
       tbl_summary(
         by = HINS4,
         include = c(CIT, LTINU,  RACE1,SEX,ESRG, MARG, SCHLG,POVPIPG, ENG, CORIGIN, DIS,CULRG) ,
         label = list (
           RACE1~"Race/ethnicity", CIT~"Citizenship status",LTINU ~"Lifetime in US",
           SEX ~ "Sex", DIS ~"Disability", ESRG~"Current employment status", MARG ~"Marital status",
           SCHLG~"Education" , POVPIPG ~ "Federal poverty",ENG~"Self-rated English proficiency",
           CORIGIN~"Country/Region of birth", CULRG~"Cultural clusters"
         ), 
         percent = "row",
         statistic = list(all_categorical() ~ "{p}%")
       ) %>%
       modify_column_hide(columns = stat_1) %>%
       italicize_labels() #%>
   )
 
 
 table4 <- tbl_merge(
                tbls = list(t1, t2),
                tab_spanner = c("**Expansion**", "**Non-expansion**")
                  )%>%
                 modify_header(
                        stat_2_1_1 = "**Pre-ACA** ({style_percent(p)}%)",
                        stat_2_2_1 = "**Post-ACA** ({style_percent(p)}%)",
                        stat_2_1_2 = "**Pre-ACA** ({style_percent(p)}%)",
                        stat_2_2_2 = "**Post-ACA** ({style_percent(p)}%)"
                              ) %>%
                 modify_caption("**Table 4. Medicaid coverage rate before/after ACA for expansion/non-expansion state by characteristics**")
 
as_kable(table4, format = "latex")

```

### Table 5: Uninsured Rate by Socio-Demographic Factors, Across Citizenship Status
```{r table-5}
 table5<-Data %>%  select(UNINS,SEX, DIS, ESRG, MARG ,SCHLG , RACE1,POVPIPG,
                           CIT,LTINU,ENG, CULRG,CORIGIN ) %>%
    tbl_strata(
      strata = CIT,
      .tbl_fun = ~ .x %>% 
        tbl_summary(
          by = UNINS,
          missing = "no" ,
          label = list(SEX ~ "Sex", DIS ~"Disability",
                      ESRG~"Current employment status",
                      SCHLG~"Education" , RACE1~"Race/ethnicity",CULRG~"Cultural clusters",
                      POVPIPG ~ "Federal poverty",LTINU ~"Lifetime in US",
                      ENG~"Self-rated English proficiency", CORIGIN~"Country/Region of birth"
                      ),
          percent = "row",
          statistic = list(all_categorical() ~ "{p}%")
                   ) %>%
         
            # add_p() %>%
            # add_significance_stars(hide_ci = TRUE, hide_p = TRUE)%>%
            italicize_labels() %>%
             bold_labels() %>%
             modify_column_hide(columns = stat_1) %>%
             modify_header(stat_2 = "{style_percent(p)}%") %>%
             modify_spanning_header(stat_2 ~ "**Expansion**")%>%
        
              modify_caption("**Table 5. Uninsured Rate by Socio-Demographic Factors, Across Citizenship Status**")
      
      
      #.header = "**{strata}**, N = {n}"
    )
as_kable(table5, format = "html")

```

### Table 6: Medicaid Coverage Rate by Socio-Demographic Factors, Across Citizenship Status
```{r table-6}
 table6<-Data %>%  select(HINS4, SEX, DIS, ESRG, MARG ,SCHLG , RACE1,POVPIPG,
                           CIT,LTINU,ENG, CULRG,CORIGIN ) %>%
    tbl_strata(
      strata = CIT,
      .tbl_fun = ~ .x %>% 
        tbl_summary(
          by = HINS4,
          missing = "no" ,
          label = list(SEX ~ "Sex", DIS ~"Disability",
                       ESRG~"Current employment status",
                       SCHLG~"Education" , RACE1~"Race/ethnicity",CULRG~"Cultural clusters",
                       POVPIPG ~ "Federal poverty",LTINU ~"Lifetime in US",
                       ENG~"Self-rated English proficiency", CORIGIN~"Country/Region of birth"
          ),
          percent = "row",
          statistic = list(all_categorical() ~ "{p}%")
        ) %>%
        
        # add_p() %>%
        # add_significance_stars(hide_ci = TRUE, hide_p = TRUE)%>%
        italicize_labels() %>%
        bold_labels() %>%
        modify_column_hide(columns = stat_1) %>%
        modify_header(stat_2 = "{style_percent(p)}%") %>%
        modify_caption("**Table 6. Medicaid Coverage Rate by Socio-Demographic Factors, Across Citizenship Status**")
      
      
      #.header = "**{strata}**, N = {n}"
    )
knitr::kable(table6)  # NA is displayed by default

```



