---
title: "Descriptive"
author: "Shadi"
date: "2023-06-20"
output:
  pdf_document:
    keep_tex: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
---


```{r data, include=FALSE}

load(paste0(wd$data,"Data.Rdata"))
Forgn<- Data[Data$NATIVITY == "Foregin-born", ]
NATV<- Data[Data$NATIVITY == "US-born", ]

```


```{r library ,  include=FALSE}
library(knitr)

library(tidyverse)
library(gtsummary)
library(survey)
library(gt)
library('kableExtra')
library(flextable)

```

```{r svydesign}
svy <- svydesign(
                  id=~1,
                  weights = ~ PWGTP, 
                  repweights = ~ matches("PWGTP[0-9]+"), 
                  data = Data, 
                  type = "JK1",
                  scale = 4/80,
                  rscales = rep(1, 80),
                  mse = TRUE
            )

```

### Table 1: Baseline Characteristics for states


```{r table-1 }

t1<-Data %>% 
        filter(ACA=="Pre-ACA")%>%
        select(ADA,IPC, UnempR,expansion) %>%
            tbl_summary(
                    by = expansion,
                    label = list(ADA ~ "State's Political Liberalism",
                                 UnempR ~"State's Unemployment Rate",
                                 IPC ~ "Immigration Policy Climate"
                                  ),
                     statistic = list(all_continuous() ~ "{mean} ({sd})")
                     )%>%
                      add_difference() %>%
                      add_significance_stars(
                                    pattern= "{estimate}{stars}",
                                    hide_ci = TRUE,
                                    hide_p = TRUE
                                         ) %>%
                      modify_table_styling(
                                   columns = estimate,
                                   rows = p.value < 0.05,
                                   text_format = "bold"
                                      )%>%
  
                     # modify_spanning_header(all_stat_cols() ~ "**Table 1.Baseline Comparison of States**") %>%
                      modify_header(
                                  label = "**Variable**",
                                  stat_1 = '**Non Expansion**',
                                   stat_2 = '**Expansion**'
                             )
# tab1 # check if all is correct

# create post-aca table for states variable

t2<-Data %>% 
  filter(ACA=="Post-ACA")%>%
  select(ADA,IPC, UnempR,expansion) %>%
  tbl_summary(
    by = expansion,
    label = list(ADA ~ "State's Political Liberalism",
                 UnempR ~"State's Unemployment Rate",
                 IPC ~ "Immigration Policy Climate"
    ),
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  )%>%
  add_difference() %>%
   add_significance_stars(
                            pattern= "{estimate}{stars}",
                            hide_ci = TRUE,
                            hide_p = TRUE
                       ) %>%
   modify_table_styling(
     columns = estimate,
     rows = p.value < 0.05,
     text_format = "bold"
   )%>%
  
  modify_caption("Baseline Comparison of States") %>%
  # modify_spanning_header(all_stat_cols() ~ "**Table 1.Baseline Comparison of States**") %>%
  modify_header(
    label = "**Variable**",
    stat_1 = '**Non Expansion**',
    stat_2 = '**Expansion**'
  )


#tab2 # check if everything is correct

## Stack two tables to create table 1

table1 <-
 
     tbl_stack(list(t1, t2), group_header = c('Pre-ACA', 'Post-ACA'))

#table1 %>% 
  
#  as_flex_table() %>% flextable::valign() didn't align
  
# as_hux_table(table1) # %>% huxtable::to_latex() gave latex code

# as_gt() %>% gt::as_latex() 
table1 %>% 
 as_kable_extra(booktabs = TRUE,
    longtable = TRUE,
    linesep = "") %>% 
  kableExtra::kable_styling(latex_options= "scale_down",font_size=6.5) %>%
       column_spec(1,bold=TRUE) %>%
          row_spec(3,hline_after=TRUE)


```

### Table 2: Baseline Characteristics by Nativity

Table 2 provides a comprehensive summary of the demographic characteristics, insurance rates, and Medicaid coverage of the low-income adult sample  prior to the implementation of the Affordable Care Act. It includes the pre-expansion means for age and proportions of various variables, specifically distinguishing between foreign-born and US-born individuals in states that expanded their Medicaid later and non-expansion states that did not expand their Medicaid until 2019.

Significant differences were observed across all demographic characteristics between foreign-born and US-born adults. However, while substantial disparities were found between native and foreign-born individuals in both expansion and non-expansion states, the discrepancies between native-born individuals in expansion and non-expansion states were relatively smaller in magnitude. The same trend was observed for foreign-born individuals.


For example, in the expansion state, the proportion of foreign-born individuals who identified as Hispanic was 68%, compared to 76% in non-expansion states. This reveals that the non-expansion states had approximately 6.7% more foreign-born Hispanics compared to the expansion state. Additionally, the proportion of US-born Hispanics in the expansion state was 11%, while this population was only 1% lower in non-expansion states. Notably, within both expansion and non-expansion states, the disparities between foreign-born andUS-born individuals were more pronounced. Specifically, approximately 66% of the foreign-born population in the expansion state identified as Hispanic, while only 9.7% of the US-born population shared this heritage, resulting in a significant difference of about 57%.


```{r table-2 }

table2<-svy %>% subset(ACA=="Pre-ACA")%>%
      tbl_strata(
           strata = expansion,
          .tbl_fun = ~ .x %>% 
                tbl_svysummary(
                         by = NATIVITY,
                         include = c(
                                 UNINS, HINS4, AGEP, SEX,  DIS, 
                                 ESRG, MARG ,SCHLG , RACE1,POVPIPG,
                                 CIT,LTINU,ENG,CULRG,CORIGIN 
                                     ),
                         missing = "no",
                         label = list(
                               AGEP ~ "Age", UNINS ~ "Uninsured",
                               HINS4 ~ "Medicaid coverage", SEX ~ "Sex", DIS ~"Disability",
                               ESRG~"Current employment status", MARG ~"Marital status",
                               SCHLG~"Education" , RACE1~"Race/ethnicity",POVPIPG ~ "Federal poverty",
                               CIT~"Citizenship status",LTINU ~"Lifetime in US",
                               ENG~"Self-rated English proficiency", 
                               CORIGIN~"Country/Region of birth", CULRG~"Cultural clusters"
                                     )
                              ) %>%
                add_p()                  %>%
                  #add_p (
                  # perform t-test for all variables
                  #test = list(all_continuous() ~ "t.test", all_categorical() ~ "chisq.test"),
                  # assume equal variance in the t-test
                  # test.args = all_tests("t.test") ~ list(var.equal = TRUE)
                        #)                 %>%
               add_significance_stars(hide_ci = TRUE, hide_p = FALSE)%>%
               bold_labels() %>%
               modify_caption("Baseline Characteristics by Nativity") %>%
               modify_header(all_stat_cols() ~ "**{level}**, {n}")
              #modify_spanning_header(stat_1 ~ "**Non Expansion**", stat_2 ~ "**Expansion**")
            )
table2 %>% 
  
as_kable_extra(booktabs = TRUE,
                   longtable = TRUE,
                   linesep = ""
                  # col.names=linebreak(c("","Born in US\n Territories","Born in\n US states", 
                  # "Naturalized \n citizen",'Non-citizen' ,"US-citizen\n Born abroad"),align="c")
    ) %>% 
    kableExtra::kable_styling(latex_options= c("scale_down","repeat_header"), font_size=6)%>%
       column_spec(1,width="3 cm")  %>%
        column_spec(2:6,width="1.8cm") 
  #  column_spec(2:11,width="1cm") 
  
  
```

### Table 3: Uninsured and Medicaid coverage rate before and after ACA for expansion and non-expansion state by characteristics

```{r tab1, include=FALSE}

t1<- Data %>% 
      filter(expansion=="expansion")%>%
      select(UNINS, CIT, LTINU,  RACE1, SEX,ESRG, MARG, SCHLG,POVPIPG, ENG,CULRG, CORIGIN, DIS,expansion,ACA) %>%  
      tbl_strata(
           strata = ACA,
          .tbl_fun = ~ .x %>%  
                  tbl_summary(
                        by = UNINS,
                        include = c(CIT, LTINU,  RACE1,SEX,ESRG, MARG, SCHLG,POVPIPG, ENG, CORIGIN, DIS,CULRG) ,
                        label = list(
                                     RACE1~"Race/ethnicity", CIT~"Citizenship status",LTINU ~"Lifetime in US",
                                     SEX ~ "Sex", DIS ~"Disability", ESRG~"Current employment status", MARG ~"Marital status",
                                     SCHLG~"Education" , POVPIPG ~ "Federal poverty",ENG~"Self-rated English proficiency",
                                     CORIGIN~"Country/Region of birth", CULRG~"Cultural clusters"
                                     ), 
                        percent = "row",
                        statistic = list(all_categorical() ~ "{p}%")
                             ) %>%
                    modify_column_hide(columns = stat_1)%>%
                    italicize_labels() %>%
                    modify_header(label = "Characteristic")                  
                    # modify_header(stat_2 = "N = {n} ({style_percent(p)}%)") %>%
                    # modify_footnote(update = everything() ~ NA) # if you'd like no footnote remove #
                )

 t2<- Data %>% 
   filter(expansion=="Non-expansion")%>%
   select(UNINS, CIT, LTINU,  RACE1, SEX,ESRG, MARG, SCHLG,POVPIPG, ENG,CULRG, CORIGIN, DIS,expansion,ACA) %>%  
   tbl_strata(
       strata = ACA,
      .tbl_fun = ~ .x %>%  
           tbl_summary(
                      by = UNINS,
                      include = c(CIT, LTINU,  RACE1,SEX,ESRG, MARG, SCHLG,POVPIPG, ENG, CORIGIN, DIS,CULRG) ,
                      label = list (
                                RACE1~"Race/ethnicity", CIT~"Citizenship status",LTINU ~"Lifetime in US",
                                SEX ~ "Sex", DIS ~"Disability", ESRG~"Current employment status", MARG ~"Marital status",
                                SCHLG~"Education" , POVPIPG ~ "Federal poverty",ENG~"Self-rated English proficiency",
                                CORIGIN~"Country/Region of birth", CULRG~"Cultural clusters"
                                   ), 
                      percent = "row",
                      statistic = list(all_categorical() ~ "{p}%")
                     ) %>%
          modify_column_hide(columns = stat_1) %>%
          italicize_labels() %>%
           modify_header(label = "Characteristic")            )
 
# creating the merged table out of the t1 and t2
 tab1<-tbl_merge(
              tbls = list(t1, t2),
              tab_spanner = c("**Expansion**", "**Non-expansion**")
                 )%>%
               modify_header(
                 stat_2_1_1 = "Pre",
                 stat_2_2_1 = "Post",
                 stat_2_1_2 = "Pre",
                 stat_2_2_2 = "Post"
                 )

```


```{r tab2, include=FALSE}
 
t1<- Data %>% 
   filter(expansion=="expansion")%>%
   select(HINS4, CIT, LTINU,  RACE1, SEX,ESRG, MARG, SCHLG,POVPIPG, ENG,CULRG, CORIGIN, DIS,expansion,ACA) %>%  
   tbl_strata(
     strata = ACA,
     .tbl_fun = ~ .x %>%  
       tbl_summary(
         by = HINS4,
         include = c(CIT, LTINU,  RACE1,SEX,ESRG, MARG, SCHLG,POVPIPG, ENG, CORIGIN, DIS,CULRG) ,
         label = list(
           RACE1~"Race/ethnicity", CIT~"Citizenship status",LTINU ~"Lifetime in US",
           SEX ~ "Sex", DIS ~"Disability", ESRG~"Current employment status", MARG ~"Marital status",
           SCHLG~"Education" , POVPIPG ~ "Federal poverty",ENG~"Self-rated English proficiency",
           CORIGIN~"Country/Region of birth", CULRG~"Cultural clusters"
         ), 
         percent = "row",
         statistic = list(all_categorical() ~ "{p}%")
       ) %>%
       modify_column_hide(columns = stat_1)%>%
        italicize_labels() %>%
         modify_header(label = "Characteristic")
   )
     
     # modify_header(stat_2 = "N = {n} ({style_percent(p)}%)") %>%
     # modify_footnote(update = everything() ~ NA) # if you'd like no footnote remove #
   
 
 t2<- Data %>% 
   filter(expansion=="Non-expansion")%>%
   select(HINS4, CIT, LTINU,  RACE1, SEX,ESRG, MARG, SCHLG,POVPIPG, ENG,CULRG, CORIGIN, DIS,expansion,ACA) %>%  
   tbl_strata(
     strata = ACA,
     .tbl_fun = ~ .x %>%  
       tbl_summary(
         by = HINS4,
         include = c(CIT, LTINU,  RACE1,SEX,ESRG, MARG, SCHLG,POVPIPG, ENG, CORIGIN, DIS,CULRG) ,
         label = list (
           RACE1~"Race/ethnicity", CIT~"Citizenship status",LTINU ~"Lifetime in US",
           SEX ~ "Sex", DIS ~"Disability", ESRG~"Current employment status", MARG ~"Marital status",
           SCHLG~"Education" , POVPIPG ~ "Federal poverty",ENG~"Self-rated English proficiency",
           CORIGIN~"Country/Region of birth", CULRG~"Cultural clusters"
         ), 
         percent = "row",
         statistic = list(all_categorical() ~ "{p}%")
       ) %>%
       modify_column_hide(columns = stat_1) %>%
        italicize_labels() %>%
         modify_header(label = "Characteristic")
   )
 
 
 tab2 <- tbl_merge(
                tbls = list(t1, t2),
                tab_spanner = c("**Expansion**", "**Non-expansion**")
                  )%>%
                 modify_header(
                        stat_2_1_1 = "Pre",
                        stat_2_2_1 = "Post",
                        stat_2_1_2 = "Pre",
                        stat_2_2_2 = "Post"
                              )
 

```





```{r table-3}

table3<-tbl_merge(list(tab1,tab2),tab_spanner = c('Uninsured','Medicaid')) %>% 
 
 modify_caption("Uninsured/Medicaid Rate by charachterstics in expansion vs non expansion states")

# col.names=linebreak(c("","Born in US\n Territories","Born in\n US states", 
                  # "Naturalized \n citizen",'Non-citizen' ,"US-citizen\n Born abroad"),align="c")
 #  
  
 #merged_table %>% 
    
# as_kable_extra(booktabs = TRUE,
                #   longtable = TRUE,
               #    linesep = ""
                  # col.names=linebreak(c("","Born in US\n Territories","Born in\n US states", 
                  # "Naturalized \n citizen",'Non-citizen' ,"US-citizen\n Born abroad"),align="c")
 #   ) %>% 


    options(knitr.kable.NA = "")
    kbl(table3, booktabs = TRUE,
                  longtable = TRUE,
                  ) %>% 
                  
    kableExtra::add_header_above(c(" "=1,"Expansion"=2,"Non-expansion"=2,"Expansion"=2, "Non-expansion"=2))%>% 
         add_header_above(c(" "=1,"Uninsured Rate"=4,"Medicaid Coverage"=4))%>% 

    kable_styling(latex_options= c("scale_down","repeat_header"), font_size=6.5)  #%>%
   # column_spec(1,width="2cm") 

```

### Table 4: Uninsured/Medicaid Coverage Rate by Socio-Demographic Factors, Across Citizenship Status


```{r table-4}

# Create a vector of variables
  variables <- c("UNINS", "HINS4")
  
  # Create an empty list to store the tables
  tables <- list()
  
  # Iterate over the variables
  for (var in variables) {
    # Create an empty list to store the tables for each value of CIT
    cit_tables <- list()
    
    # Get unique values of CIT
    cit_values <- unique(Data$CIT)
    
    # Iterate over the values of CIT
    for (cit_value in cit_values) {
      # Filter the data based on CIT
      filtered_data <- Data %>%
        filter(CIT == cit_value) %>%
        select({{ var }}, SEX, DIS, ESRG, MARG, SCHLG, RACE1, POVPIPG,LTINU, ENG, CULRG, CORIGIN)
      
      # Create the table using tbl_summary
      table <- filtered_data %>%
        tbl_summary(
          by = all_of(var),
          missing = "no",
          label = list(
            SEX ~ "Sex",
            DIS ~ "Disability",
            ESRG ~ "Current employment status",
            SCHLG ~ "Education",
            RACE1 ~ "Race/ethnicity",
            CULRG ~ "Cultural clusters",
            POVPIPG ~ "Federal poverty",
            LTINU ~ "Lifetime in US",
            MARG ~"Married",
            ENG ~ "Self-rated English proficiency",
            CORIGIN ~ "Country/Region of birth"
          ),
          percent = "row",
          statistic = list(all_categorical() ~ "{p}%")
        ) %>%
        modify_column_hide(columns = stat_1) %>%
          bold_labels()       %>%
          modify_footnote(update = everything() ~ NA)
      # Modify the table header
      if (var == "UNINS") {
        table <- table %>%
          modify_header(stat_2 = "Uninsured {style_percent(p)}%")
      } else if (var == "HINS4") {
        table <- table %>%
          modify_header(stat_2 = "Medicaid {style_percent(p)}%")
      }
      
      # Add the table to the list for the specific value of CIT
      cit_tables[[cit_value]] <- table
    }
    
    # Add the list of tables for the variable to the main list
    tables[[var]] <- cit_tables
  }
 
  
  
  t <- list()
  
  for (cit_value in cit_values) {
  
    t[[cit_value]]  <- tbl_merge(list(tables$UNINS[[cit_value]], tables$HINS4[[cit_value]]))
    
         }
    
tables<-tbl_merge(list(t$`Non-citizen`,t$`Naturalized-citizen`,t$`US-citizen Born abroad `,
                       t$`Born in US states`,t$`Born in US Territories`),
                       tab_spanner = c("Non-citizen","Naturalized-citizen",'Citizen born abroad',
                                       'Born in US states','Born in territories')
                       ) %>% 
 modify_caption("Uninsured/Medicaid Rate by Socio-Demographic Factors, Across Citizenship Status")


 tables %>% 
    
    as_kable_extra(booktabs = TRUE,
                   longtable = TRUE,
                   linesep = ""
                  # col.names=linebreak(c("","Born in US\n Territories","Born in\n US states", 
                  # "Naturalized \n citizen",'Non-citizen' ,"US-citizen\n Born abroad"),align="c")
    ) %>% 
    kableExtra::kable_styling(latex_options= c("scale_down","repeat_header"), font_size=6)%>%
       column_spec(1,width="2.8cm") %>%

    column_spec(2:11,width="1cm") 
  



```





