---
title: "DiD-regression"
author: "Shadi"
date: "2023-07-06"
output:
  pdf_document:
    keep_tex: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
---



```{r setup , include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.align = "center",
                      fig.width = 8, 
                      fig.height = 4, 
                      fig.path = "figures/prefix-",
                      dpi = 200,
                      dev = "png",
                       warning=FALSE,
                      message=FALSE 
                      )


```



```{r wd-setup, include=FALSE}

wd <- list()
# commonly used paths in my working directory
wd$data   <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/data/"
wd$output <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/output/"
wd$texts <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/texts"
wd$codes <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/codes/R/"

```

```{r}
Data<-read.csv( paste0(wd$data,"CLNACS.csv"), header = TRUE, sep = ",", fill = TRUE, stringsAsFactors = TRUE)

controls <- c("SEX","DIS", "AGEP","MARG", "SCHLG", "RACE1","ESRG","POVPIPG",'CIT')
foriegn <- c( "ENG", "LTINU", "CORIGIN" )
adjs<-c("UnempR", "ADA")
adj12<-c("UnempR", "ADA","IPC")
```




```{r library-setup, include=FALSE}
library(fixest)


```

```{r data-setup}

  # create a dummy for foreign-born
Data$ForeginBorn <- ifelse(Data$NATIVITY == "Foregin-born", 1, 0)
# Make sure data are factor
data<-Data
factor_columns <- sapply(data, is.factor)
data[factor_columns] <- lapply(data[factor_columns], as.character)

data <- replace(data, is.na(data), 99999999)

data[factor_columns] <- lapply(data[factor_columns], as.factor)


```


We first examine the effect of medicaid expansion on uninsured rate. Table 2 presents the primary findings of the DD analysis, employing sample weights and adjusting for covariates. the first 7 columns show estimates from the fixed effect logistic regression,  while the second seven columns show results from OLS. Each specification controls for state and year fixed effects. Column 2 controls for the variables state political ideology and state unemployment rate which were the minimal adjustment set based on the DAG result. Column 3  additionally controls for region-by-year fixed effects while column 4 control for state-specific linear time trends. the full model with all the control variables added are presented in columns 5-7, the difference is in column 6 region-by-year fixed effects is added whereas in column 7 state-specific linear time trend is added.


Columns numbers reveal a positive and statistically significant association between Medicaid expansion and hospital Medicaid revenue. For hospitals in Medicaid-expansion states, Medicaid net revenue increased, on average, by 2.67% after Medicaid expansion (column 3). Meanwhile, columns 4 - 6 shows Medicaid expansion decreased hospital uncompensated care cost by approximately 2%, which is statistically and economically significant.

For both populations, the “Post X Expansion” term was positive and statistically significant for “any insurance” (p<.01) and “Medicaid” (p<.001), suggesting that Medicaid expansion resulted in a significant increase in the probability of having any insurance and having Medicaid for urban and rural low-income populations pooled.

Put differently, our estimates and standard errors from column 2 




```{r tablereg, results='asis'}


reg1 = feols(UNINS ~treat*ForeginBorn | ST + YEAR , cluster = ~ST, weights = ~PWGTP, data = data) # state and year fixed effect
reg2 = feols(UNINS ~treat*ForeginBorn+.[adjs]  | ST + YEAR+ sw0(REGION^YEAR) , cluster = ~ST, weights = ~PWGTP, data = data) # state and year fixed effect
reg3 = feols(UNINS ~treat*ForeginBorn+.[adjs]  | ST + YEAR + ST[YEAR], cluster = ~ST, weights = ~PWGTP, data = data) # state and year fixed effect

reg4 = feols(UNINS ~ treat*ForeginBorn + ForeginBorn*.[controls]+ ForeginBorn*.[foriegn]| ST + YEAR +sw0(REGION^YEAR), cluster = ~ST, weights = ~PWGTP, data = data) # state and year fixed effect

reg5 = feols(UNINS ~ treat*ForeginBorn + ForeginBorn*.[controls]+ ForeginBorn*.[foriegn] | ST + YEAR + ST[YEAR], cluster = ~ST, weights = ~PWGTP, data = data) # state and year fixed effect

table3<-
  etable(list(reg1,reg2,reg3, reg4,reg5), 
          group = list("^_Controls"=c(controls,foriegn)),
          digits = 3,
          vcov = "twoway", 
          depvar=FALSE,
          dict=c("UnempR"= "state unemployment rate", "ADA"="State Political Ideology"),
          style.tex = style.tex(
                             main = "base",
                             fixef.suffix = " FE",
                             fixef.title = " ",
                              stats.title = "",
                            # tabular = "*",
                               model.title = "Variables",
                               depvar.title= " ",
                               var.title = "\\midrule \\",
                              yesNo = "yes")
)

table3


```


Table number reports empirical finding regarding the effect of medicaid expansion on medicaid coverage among low income adult. 
