---
title: "DiD-regression"
author: "Shadi"
date: "2023-07-06"
output:
  pdf_document:
    keep_tex: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{adjustbox}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \setkeys{Gin}{width=\linewidth,height=\textheight,keepaspectratio}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \pagenumbering{gobble}
---


```{r library-did, include=FALSE}
library(fixest)

```

```{r data-did}

  # create a dummy for foreign-born
Data$ForeginBorn <- ifelse(Data$NATIVITY == "Foregin-born", 1, 0)
# Make sure data are factor
data<-Data
factor_columns <- sapply(data, is.factor)
data[factor_columns] <- lapply(data[factor_columns], as.character)

data <- replace(data, is.na(data), 99999999)

data[factor_columns] <- lapply(data[factor_columns], as.factor)


```

We first examine the effect of Medicaid expansion on the uninsured rate. Table 7 presents the primary findings of the difference-in-differences (DD) analysis, which includes sample weights and adjusts for covariates. The first seven columns display estimates from the fixed effect linear probability model, while the second seven columns show results from the fixed effect logit model. Each specification controls for state and year fixed effects.

Column 2 includes controls for state political ideology and state unemployment rate, which were identified as the minimal adjustment set based on the result of the directed acyclic graph (DAG) causal discovery. Column 3 additionally controls for region-by-year fixed effects, while column 4 controls for state-specific linear time trends. The full model with all the control variables added is presented in columns 5-7, where column 6 includes region-by-year fixed effects and column 7 includes state-specific linear time trends.

Among FE OLS models, the estimated effect of Medicaid expansion on the uninsured ranges from -0.044 to -0.092 across different specifications (columns 1 to 7). These estimates suggest that Medicaid expansion reduces the probability of being uninsured by approximately 4.4% to 9.2%. Among FE LOGIT model, the estimated effect ranges from -0.333 to -0.629 across different specifications (columns 8 to 14). Since the FE LOGIT model estimates the effect in terms of odds ratios, the estimates suggest that Medicaid expansion reduces the odds of being uninsured by approximately 33.3% to 62.9%.


Furthermore, the models indicate that being foreign-born is associated with an increase in the probability of being uninsured in the FE OLS model, while it increases the odds of being uninsured in the FE LOGIT model. Both models show a negative and statistically significant interaction term, indicating that the effect of Medicaid expansion on the uninsured rate is smaller for foreign-born individuals compared to the US-born population.

To assess the goodness of fit of the models, we consider the adjusted R-squared for the FE OLS model and the Pseudo R-squared and BIC for both models. The FE OLS model in column 7 exhibits the highest adjusted R-squared value of 0.17830 and the lowest BIC value of 2,206,836.9. For the FE LOGIT model, column 14 has the highest Pseudo R-squared value of 0.15066 and the lowest BIC value of 240,927,239.1.

These measures help evaluate the fit of the models to the data, with higher adjusted R-squared and Pseudo R-squared values indicating better fit, and lower BIC values suggesting better model performance.


We examine the effect of Medicaid expansion on the Medicaid coverage rate. Table 8 presents the primary findings of the difference-in-differences (DD) analysis, including sample weights and covariate adjustments. The table consists of two sets of estimates: the fixed effect (FE) OLS model in the first seven columns and the FE logit model in the second seven columns. Both models control for state and year fixed effects.

In the FE OLS model, the estimated effect of Medicaid expansion on the Medicaid coverage rate ranges from 0.085 to 0.148 across different specifications (columns 1 to 7). These estimates indicate that Medicaid expansion increases the rate of individuals covered by Medicaid by approximately 8.5% to 14.8%. Similarly, in the FE logit model, the estimated effect ranges from 0.305 to 0.660 (columns 8 to 14), suggesting that Medicaid expansion reduces the odds of being uninsured and increases the odds of being covered by Medicaid.

We also examine the impact of foreign-born status on the Medicaid coverage rate. In the FE OLS model, being foreign-born is associated with a decrease in the Medicaid coverage rate, while in the FE logit model, it decreases the odds of being covered by Medicaid.

Furthermore, both models show a positive and statistically significant interaction term between Medicaid expansion and foreign-born status. This indicates that the effect of Medicaid expansion on the Medicaid coverage rate is larger for foreign-born individuals compared to the general population.

To assess the goodness of fit, we consider the R-squared, adjusted R-squared, pseudo R-squared, AIC, and BIC. The FE OLS model exhibits an R-squared ranging from 0.08522 to 0.08677 and an adjusted R-squared ranging from 0.08520 to 0.08672 (columns 1 to 7). In the FE logit model, the pseudo R-squared ranges from 0.99160 to 0.99241 (columns 8 to 14). Lower values of AIC and BIC indicate better model performance.

Based on these measures, the preferred model specifications in Table 8 may be column 7 in the FE OLS model and column 14 in the FE logit model. These specifications tend to have higher R-squared, adjusted R-squared, and pseudo R-squared values, as well as lower AIC and BIC values.

However, it is crucial to consider other factors, such as theoretical relevance, robustness checks, and the specific research context, when selecting the most appropriate model for analysis.




> ***To DO Shadi:*** The BIC and Pseudo R-squared are off check why is that. Given that LOGIT is prefered over PLM should I choose col 14 as my prefered model? should I add or remove any specificaiton?


```{=tex}
\newpage
\blandscape
```

```{r tablereg, results='asis'}

# this is where I found good info on how to rotate the table # # #"https://stackoverflow.com/questions/25849814/rstudio-rmarkdown-both-portrait-and-landscape-layout-in-a-single-pdf

reg1 = feols(UNINS ~treat*ForeginBorn | ST + YEAR , vcov = "hetero", weights = ~PWGTP, data = data) # state and year fixed effect
reg2 = feols(UNINS ~treat*ForeginBorn+.[adjs]  | ST + YEAR+ sw0(REGION^YEAR) , vcov = "hetero", weights = ~PWGTP, data = data) # state and year fixed effect
reg3 = feols(UNINS ~treat*ForeginBorn+.[adjs]  | ST + YEAR + ST[YEAR], vcov = "hetero", weights = ~PWGTP, data = data) # state and year fixed effect

reg4 = feols(UNINS ~ treat*ForeginBorn + ForeginBorn*.[controls]+ ForeginBorn*.[foriegn]| ST + YEAR +sw0(REGION^YEAR), vcov = "hetero", weights = ~PWGTP, data = data) # state and year fixed effect

reg5 = feols(UNINS ~ treat*ForeginBorn + ForeginBorn*.[controls]+ ForeginBorn*.[foriegn] | ST + YEAR + ST[YEAR], vcov = "hetero", weights = ~PWGTP, data = data) # state and year fixed effect


reg6 = feglm(UNINS ~treat*ForeginBorn | ST + YEAR , vcov = "hetero", weights = ~PWGTP, data = data, family = 'logit') # state and year fixed effect
reg7 = feglm(UNINS ~treat*ForeginBorn+.[adjs]  | ST + YEAR+ sw0(REGION^YEAR) , vcov = "hetero", weights = ~PWGTP, data = data, family = 'logit') # state and year fixed effect
reg8 = feglm(UNINS ~treat*ForeginBorn+.[adjs]  | ST + YEAR + ST[YEAR], vcov = "hetero", weights = ~PWGTP, data = data, family = 'logit') # state and year fixed effect

reg9 = feglm(UNINS ~ treat*ForeginBorn + ForeginBorn*.[controls]+ ForeginBorn*.[foriegn]| ST + YEAR +sw0(REGION^YEAR), vcov = "hetero", weights = ~PWGTP, data = data, family = 'logit') # state and year fixed effect

reg0 = feglm(UNINS ~ treat*ForeginBorn + ForeginBorn*.[controls]+ ForeginBorn*.[foriegn] | ST + YEAR + ST[YEAR], vcov = "hetero", weights = ~PWGTP, data = data, family = 'logit') # state and year fixed effect


table3<-
  etable(list(reg1,reg2,reg3, reg4,reg5,reg6,reg7,reg8, reg9,reg0), 
          title = "The Effect of Medicaid Expansion on Uninsured Rate (Difference-in-Differences Estimation)",
          headers = list("^:_:"= .("FE OLS" = 7, "FE LOGIT"=7)),
         
         # extralines=list("^^Uninsured"=.(" ")) ,
          group = list("-^Controls"=c(controls,foriegn)),
          digits = 3,
          adjustbox= 1.5,
          tex= TRUE,
         se.row = TRUE, 
          depvar= FALSE,
          family = FALSE,
          arraystretch = 1.75,
          convergence = T,
         fitstat = ~ n +r2 +ar2 + pr2+  aic + bic ,
          # notes = c("note 1", "source 1"),
          style.tex = style.tex(
                             main = "base",
                             fixef.suffix = " FE",
                             fixef.title = "\\midrule",
                             stats.title = "\\midrule",
                            # tabular = "*",
                               model.title = "",
                             #  model.format = "[i]",
                             # fontsize= 'normalsize', 
                             tpt=T,
                               depvar.title= " ",
                               var.title = "\\midrule",
                            slopes.title = "",
                            slopes.format = "State-Specific Linear Time Trends",
                             yesNo = "yes"
                            ) ,
         dict=c(ST = "State" , YEAR = "Year", UNINS="Uninsured Rate", treat='Medicaid Expansion',
               ForeginBorn= 'Foreign-Born',UnempR= "State Unemployment Rate", ADA="State Political Ideology", REGION="Region"
               )
)

print(table3)


```

\elandscape


We then shift our focus to analyzing the impact of Medicaid expansion on Medicaid coverage using Table 8. This table follows a similar structure to Table 7, with the FE Linear probability  model estimates in the first seven columns and the FE logit model estimates in the second seven columns. Both models include state and year fixed effects to account for potential confounding factors.

In the FE OLS model, the estimated effect of Medicaid expansion on the Medicaid coverage rate ranges from 0.085 to 0.148 across different specifications (columns 1 to 7). These estimates suggest that Medicaid expansion increases the probability of individuals being covered by Medicaid by approximately 8.5% to 14.8%. Similarly, in the FE logit model, the estimated effect ranges from 0.305 to 0.660 (columns 8 to 14), indicating that Medicaid expansion increases the odds of being covered by Medicaid.

We also examine the impact of foreign-born status on the Medicaid coverage rate. In the FE OLS model, being foreign-born is associated with a  decreased probability in having Medicaid coverage, while in the FE logit model, it decreases the odds of being covered by Medicaid.

Moreover, the interaction term between Medicaid expansion and foreign-born status shows a significant relationship in both models. However, the magnitude and direction of this interaction term vary across different models and specifications. In columns 5, 6, and 7 of the table, negative coefficients are observed for the interaction term between Medicaid expansion and foreign-born status. This indicates that in those specific model specifications, the effect of Medicaid expansion on the Medicaid coverage rate is smaller for foreign-born individuals compared to the US-born population.

For example, in column 1 and 5, the coefficient of the interaction term is positive but small in magnitude, suggesting that Medicaid expansion has a small positive effect on the probability of foreign-born individuals being covered compared to US-born individuals. However, as additional covariates are included in the model, the coefficient becomes negative in columns 6 and 7, indicating a smaller effect of Medicaid expansion for foreign-born individuals.

In the FE logit model specifications, the odds of being covered by Medicaid due to Medicaid expansion are positive for foreign-born individuals but decrease as additional covariates are included. In our preferred model (column 14), the odds are estimated to be 16%, indicating a substantial increase in the likelihood of Medicaid coverage for foreign-born individuals due to Medicaid expansion.


Similar to table-7 we consider the R-squared, adjusted R-squared, pseudo R-squared, AIC, and BIC to eveluate the model fit. In the FE OLS model, the R-squared ranges from 0.08522 to 0.19483, and the adjusted R-squared ranges from 0.08520 to 0.19477 (columns 1 to 7). For the FE logit model, the pseudo R-squared ranges from -104.05 to 0.15944 (columns 8 to 14). Lower AIC and BIC values indicate better model performance. Thus, the preferred model specifications in Table 8 may be column 7 in the FE OLS model and column 14 in the FE logit model. These specifications tend to have higher R-squared, adjusted R-squared, and pseudo R-squared values, as well as lower AIC and BIC values.

Similar to Table 7, we assess the goodness of fit using R-squared, adjusted R-squared, pseudo R-squared, AIC, and BIC. In the FE OLS model, the R-squared ranges from 0.08522 to 0.19483, and the adjusted R-squared ranges from 0.08520 to 0.19477 (columns 1 to 7). For the FE logit model, the pseudo R-squared ranges from -104.05 to 0.15944 (columns 8 to 14). Lower AIC and BIC values indicate better model performance. Based on these measures, the preferred model specifications in Table 8 may be column 7 in the FE OLS model and column 14 in the FE logit model. These specifications exhibit higher R-squared, adjusted R-squared, and pseudo R-squared values, as well as lower AIC and BIC values, indicating better fit and performance.


```{=tex}
\newpage
\blandscape
```
```{r tablemedic, results='asis'}


reg1 = feols(HINS4 ~treat*ForeginBorn | ST + YEAR , vcov = "hetero", weights = ~PWGTP, data = data) # state and year fixed effect
reg2 = feols(HINS4 ~treat*ForeginBorn+.[adjs]  | ST + YEAR+ sw0(REGION^YEAR) , vcov = "hetero", weights = ~PWGTP, data = data) # state and year fixed effect
reg3 = feols(HINS4 ~treat*ForeginBorn+.[adjs]  | ST + YEAR + ST[YEAR], vcov = "hetero", weights = ~PWGTP, data = data) # state and year fixed effect

reg4 = feols(HINS4 ~ treat*ForeginBorn + ForeginBorn*.[controls]+ ForeginBorn*.[foriegn]| ST + YEAR +sw0(REGION^YEAR), vcov = "hetero", weights = ~PWGTP, data = data) # state and year fixed effect

reg5 = feols(HINS4 ~ treat*ForeginBorn + ForeginBorn*.[controls]+ ForeginBorn*.[foriegn] | ST + YEAR + ST[YEAR], vcov = "hetero", weights = ~PWGTP, data = data) # state and year fixed effect


reg6 = feglm(HINS4 ~treat*ForeginBorn | ST + YEAR , vcov = "hetero", weights = ~PWGTP, data = data, family = 'logit') # state and year fixed effect
reg7 = feglm(HINS4 ~treat*ForeginBorn+.[adjs]  | ST + YEAR+ sw0(REGION^YEAR) , vcov = "hetero", weights = ~PWGTP, data = data, family = 'logit') # state and year fixed effect
reg8 = feglm(HINS4 ~treat*ForeginBorn+.[adjs]  | ST + YEAR + ST[YEAR],vcov = "hetero", weights = ~PWGTP, data = data, family = 'logit') # state and year fixed effect

reg9 = feglm(HINS4 ~ treat*ForeginBorn + ForeginBorn*.[controls]+ ForeginBorn*.[foriegn]| ST + YEAR +sw0(REGION^YEAR), cluster = ~ST, weights = ~PWGTP, data = data, family = 'logit') # state and year fixed effect

reg0 = feglm(HINS4 ~ treat*ForeginBorn + ForeginBorn*.[controls]+ ForeginBorn*.[foriegn] | ST + YEAR + ST[YEAR], vcov = "hetero", weights = ~PWGTP, data = data, family = 'logit') # state and year fixed effect



table4<-
  etable(list(reg1,reg2,reg3, reg4,reg5,reg6,reg7,reg8, reg9,reg0), 
          title = "The Effect of Medicaid Expansion on Medicaid Covergare Rate (Difference-in-Differences Estimation)",
          headers = list("^:_:"= .("FE OLS" = 7, "FE LOGIT"=7)),
         
         # extralines=list("^^Uninsured"=.(" ")) ,
          group = list("-^Controls"=c(controls,foriegn)),
          digits = 3,
          vcov = "hetero",
           adjustbox= 1.5,
          tex= TRUE,
          depvar= FALSE,
          family = FALSE,
          arraystretch = 1.75,
          convergence = T,
          se.row = TRUE, 

          fitstat = ~ n +r2 +ar2 + pr2+  aic + bic ,
          # notes = c("note 1", "source 1"),
          style.tex = style.tex(
                             main = "base",
                             fixef.suffix = " FE",
                             fixef.title = "\\midrule",
                             stats.title = "\\midrule",
                            # tabular = "*",
                               model.title = "",
                             #  model.format = "[i]",
                              fontsize= 'large', 
                             tpt=T,
                               depvar.title= " ",
                               var.title = "\\midrule",
                            slopes.title = "",
                            slopes.format = "State-Specific Linear Time Trends",
                             yesNo = "yes"
                            ) ,
         dict=c(ST = "State" , YEAR = "Year", UNINS="Uninsured Rate", treat='Medicaid Expansion',
               ForeginBorn= 'Foreign-Born',UnempR= "State Unemployment Rate", ADA="State Political Ideology", REGION="Region"
               )
)

print(table4)



```

\elandscape

Table number reports empirical finding regarding the effect of medicaid expansion on medicaid coverage among low income adult.

For both populations, the "Post X Expansion" term was positive and statistically significant for "any insurance" (p\<.01) and "Medicaid" (p\<.001), suggesting that Medicaid expansion resulted in a significant increase in the probability of having any insurance and having Medicaid for urban and rural low-income populations pooled.