---
title: "Analysis"
author: "Shadi"
date: "2023-05-16"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
    bibliography: references.json
  chunk_output_type: inline
---

```{r setup , include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.align = "center",
                      fig.width = 4, 
                      fig.height = 4, 
                      fig.path = "figures/prefix-",

                      dev = "png",
                      cache = TRUE
                      )


```

```{r library, include=FALSE}
library(fixest)
library(ggpubr)
library(ggiplot)
library(gsl)
library(energy)
library(devtools)
library(pcalg)
library(kpcalg)
#library(CAM)
library(bnlearn)
#library(AlphaPart)
#library(tabuSearch)
#library(dplyr)
library(Rgraphviz)
library(AlphaPart)
library(brew)
library(dplyr)
library(dagitty)
library(ggdag)
#library(kableExtra)
library(pander)
library(survey)
#install.packages("srvyr")
library("srvyr")
library(gtsummary)
library(tidyverse)
library(tidycensus)
library(purrr)

```

```{r wd-setup, include=FALSE}

wd <- list()
# commonly used paths in my working directory
wd$data   <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/data/"
wd$output <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/output/"
wd$texts <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/texts"
wd$codes <- "/home/shadi/Projects/GitHub/medicaid-foreign-born/codes/R/"

```
 if you want the code to show up in your knitted file without any messages or warnings, you can write message = FALSE and warning = FALSE in the chunk header:




```{r read-data, include=FALSE}
ACS<-read.csv(paste0(wd$data,"CLNACS.csv"), header = TRUE, sep ="," , fill = TRUE)
Data<-ACS
save(Data, file = paste0(wd$data,'Data.Rdata'))
Forgn<- Data[Data$NATIVITY == "Foregin-born", ]
NATV<- Data[Data$NATIVITY == "US-born", ]


controls <- c("SEX","DIS", "AGEP","MARG", "SCHLG", "RACE1","ESRG","POVPIPG")
foriegn <- c( "ENG", "PLIU", "GEOR","IPCINDX" )
adj1<-c("UnempR", "ADA")
adj12<-c("UnempR", "ADA","CIT")

```

## Causal Structure Discovery

I utilized causal structure discovery techniques to accurately represent
the data generating process and unveil the underlying causal
relationships among the variables. The causal structure discovery
approach identifies potential causal relationships based on patterns and
dependencies observed in the data. The resulting Directed Acyclic Graph
(DAG) from the causal discovery is capturing the complex interplay
between the variables, accounting for confounding factors and potential
biases, and providing credible evidence for the causal effects of
medicaid expansion on medicaid take-up and uninsured rate.

By utilizing the DAG obtained through the causal discovery approach, I
can conduct backdoor and front door analyses, enabling the
identification of the minimal adjustment set. The minimal adjustment set
represents the smallest subset of variables that must be controled for
to obtain unbiased estimates of causal effects.

In the initial phase of our analysis, a DAG , as shown in Graph 1, was
generated using multiple constraint-based and score-based algorithms
including GDS algorithms, Greedy Equivalence Search (GES), Peter-Clark
(PC) algorithm, and Fast Causal Inferences (FCI). To integrate the
information obtained from these algorithms, following Joe et al.(2023) I
employed a majority voting approach. This involved considering each edge
and determining its presence in the final graph based on whether it
appeared in more than 50% of the cases, indicating agreement among the
majority of the algorithms.

```{r DAG1, echo=FALSE}

data1 <- subset(Data, select = c(IPC,IPCINDX,ENG,GEOR,YLIU,PLIU,CULRG, SEX,DIS,AGEP, SCHLG, MARG, ESRG, RACE1,POVPIP,treat,UnempR,ADA,CIT,HINS4))
data2 <- subset(Forgn, select = c(IPC,IPCINDX,ENG,GEOR,YLIU,PLIU,CULRG, SEX,DIS,AGEP, SCHLG, MARG, ESRG, RACE1,POVPIP,treat,UnempR,ADA,CIT,HINS4))
data3 <- subset(Data, select = c(IPC,IPCINDX,ENG,GEOR,YLIU,PLIU,CULRG, SEX,DIS,AGEP, SCHLG, MARG, ESRG, RACE1,POVPIP,treat,UnempR,ADA,CIT,UNINS))
data4 <- subset(Forgn, select = c(IPC,IPCINDX,ENG,GEOR,YLIU,PLIU,CULRG, SEX,DIS,AGEP, SCHLG, MARG, ESRG, RACE1,POVPIP,treat,UnempR,ADA,CIT,UNINS))

####################
## Identify Causal Graph
####################
variables = names(data1)
colnames(data1) = c(1:ncol(data1))
# Create an empty list to store the matrices

matMajVotingList <- list()

# Loop through data1 to data4
for (i in 1:4) {
        # Get the current data
        currentData <- get(paste0("data", i))
        
        # Convert character variables to factors
        currentData <- currentData %>% mutate_if(is.character, as.factor)
        
        # Convert factor variables to numeric
        currentData <- currentData %>% mutate_if(is.factor, as.numeric)
        
        # 1.Perform the GES algorithm
        score <- new("GaussL0penObsScore", currentData)
        ges1.fit <- ges(score, fixedGaps = NULL, adaptive = "vstructures", phase = "forward", maxDegree = integer(0), verbose = FALSE)
        
        # Create the matrix for GES algorithm
        p <- dim(currentData)[2]
        matGES <- matrix(0, nrow = p, ncol = p)
        row <- 1
        for (list in ges1.fit$essgraph$.in.edges) {
                for (node in list) {
                        matGES[node, row] <- 1
                }
                row <- row + 1
        }
        
        # 2. Perform the GDS algorithm
        gds.fit <- gds(score, fixedGaps = NULL, adaptive = "triples", phase = "forward", maxDegree = integer(0), verbose = FALSE)
        
        # Create the matrix for GDS algorithm
        matGDS <- matrix(0, nrow = p, ncol = p)
        row <- 1
        for (list in gds.fit$essgraph$.in.edges) {
                for (node in list) {
                        matGDS[node, row] <- 1
                }
                row <- row + 1
        }
        
        # 3. Perform the PC algorithm
        SuffStat <- list(C = cor(currentData), n = nrow(currentData))
        result.pc <- pc(suffStat = SuffStat, indepTest = gaussCItest, labels = colnames(currentData), alpha = 0.01)
        
        # Create the matrix for PC algorithm
        matPC <- matrix(0, nrow = p, ncol = p)
        row <- 1
        for (list in result.pc@graph@edgeL) {
                for (node in list) {
                        matPC[node, row] <- 1
                }
                row <- row + 1
        }
        
        # 4.Perform the RFCI algorithm
        result.rfci <- rfci(SuffStat, indepTest = gaussCItest, p = ncol(currentData), alpha = 0.01)
        
        # Create the matrix for RFCI algorithm
        matRFCI <- matrix(0, nrow = p, ncol = p)
        item <- 0
        for (l in result.rfci@amat) {
                row <- item %% p + 1
                column <- as.integer(item / p) + 1
                if (l == 2)
                        matRFCI[row, column] <- 1
                if (l == 3)
                        matRFCI[column, row] <- 1
                item <- item + 1
        }
        
        # Majority voting of the DAG
        matMajVoting <- matGES + matGDS + matPC + matRFCI
        
        # Store the matrix in the list
        matMajVotingList[[i]] <- matMajVoting
}

# Access the matrices from the list
matMajVoting1 <- matMajVotingList[[1]]
matMajVoting2 <- matMajVotingList[[2]]
matMajVoting3 <- matMajVotingList[[3]]
matMajVoting4 <- matMajVotingList[[4]]

MajVoting <- matMajVoting1 + matMajVoting2 + matMajVoting3 + matMajVoting4

#MajVotingF <- matMajVoting2 + matMajVoting4

# create a DAG based on majority voting 

digraph <- "dag {"  # Initialize the digraph as an empty string

for(i in 1:p){
        for(j in 1:p){
                if(MajVoting[i, j] > 8){ # change the value 2 to an appropriate value (threshold)
                        #print(variables[i])
                        digraph <- paste0(digraph, variables[i], "->", variables[j],";")
                }
        }
}

digraph <- gsub(";$", "}", digraph) # change the last ; to } to make it compatible for Dagitty function 

# create DAG object
dag <- dagitty(digraph)

# DAG representation
ggdag(dag)+  # Turn off legend
        theme_dag()+
scale_color_manual(na.value ="#222D5a") 


```

To enhance the accuracy of the causal relationships represented in the
DAG, I carefully reviewed and manually edited the graph by removing
paths that contradicted my domain knowledge or appeared implausible
within the context. By applying these revisions, the resulting DAG,
illustrated in graph 2, aligns more closely with my expertise in the
field and provides a more trustworthy representation of the underlying
causal structure in my analysis.

```{r DAG2, echo=FALSE}
findag<-dagitty('dag{
 bb="-5.958,-4.932,7.16,5.438"
 "Life Lived in US" [pos="-2.079,1.854"]
 "State Political Ideology" [pos="-4.930,0.020"]
 "Age" [pos="1.789,-1.856"]
 "Citizenship Status" [pos="-2.079,2.842"]
 "Disability" [pos="1.789,-2.675"]
 "English Proficiency" [pos="-2.079,3.801"]
 "Employment" [pos="-2.079,-3.112"]
 "Immigration Policy Climate" [pos="-4.554,2.786"]
 "Marital Status" [pos="1.811,-1.080"]
 "Income-to-Poverty Ratio" [pos="-2.068,-0.657"]
 "Race/Ethnicity" [pos="1.789,-0.107"]
 "Cultural Grouping" [pos="-2.090,4.930"]
 "Education" [pos="-2.046,-2.068"]
 "Sex" [pos="1.800,-3.676"]
 "Medicaid Take-Up" [outcome,pos="1.822,1.304"]
 "Unemployment Rate" [pos="-3.858,0.006"]
 "Medicaid Expansion" [exposure,pos="-4.389,1.276"]
 "Life Lived in US" -> "English Proficiency"
 "State Political Ideology" -> "Immigration Policy Climate"
 "State Political Ideology" -> "Unemployment Rate"
 "State Political Ideology" -> "Medicaid Expansion"
 "Age" -> "Life Lived in US"
 "Age" -> "Disability"
 "Age" -> "Employment"
 "Age" -> "Medicaid Take-Up"
 "Citizenship Status" -> "State Political Ideology"
 "Citizenship Status" -> "English Proficiency"
 "Citizenship Status" -> "Marital Status"
 "Citizenship Status" -> "Income-to-Poverty Ratio"
 "Citizenship Status" -> "Education" 
 "Citizenship Status" -> "Medicaid Take-Up"
 "Citizenship Status" -> "Employment"
 "Disability" -> "Employment"
 "Disability" -> "Education" 
 "Disability" -> "Medicaid Take-Up"
 "English Proficiency" -> "Employment"
 "English Proficiency" -> "Medicaid Take-Up"
 "Employment" -> "Income-to-Poverty Ratio"
 "Employment" -> "Medicaid Take-Up"
 "Immigration Policy Climate"  -> "Income-to-Poverty Ratio"
 "Immigration Policy Climate"  -> "Medicaid Take-Up"
 "Marital Status" -> "Income-to-Poverty Ratio"
 "Marital Status" -> "Medicaid Take-Up"
 "Income-to-Poverty Ratio" -> "Medicaid Take-Up"
 "Race/Ethnicity" -> "Education"  
 "Cultural Grouping" -> "English Proficiency"
 "Cultural Grouping" -> "Employment"
 "Cultural Grouping" -> "Race/Ethnicity"
 "Cultural Grouping" -> "Education" 
 "Cultural Grouping" -> "Medicaid Take-Up"
 "Education" -> "English Proficiency"
 "Education" -> "Employment"
 "Education" -> "Medicaid Take-Up"
 "Sex" -> "Employment"
 "Sex" -> "Medicaid Take-Up"
 "Unemployment Rate" -> "Employment"
 "Unemployment Rate" -> "Education"
 "Unemployment Rate" -> "Medicaid Take-Up"
 "Unemployment Rate" -> "Medicaid Expansion"
 "Medicaid Expansion" -> "Medicaid Take-Up"
}')

FINDAG <- ggdag_status(findag, node_size = 10, use_labels = "name", text_size = 3, label_size = 6, text = FALSE) +
  guides(color = "none") +  # Turn off legend
  theme_dag() 


FINDAG$layers[[3]]$mapping <- aes(colour = status)
FINDAG + scale_color_manual(na.value ="#222D5a" , values = c(exposure ="#A94064" , outcome = "#44AA99")) +
        scale_fill_manual(na.value ="#222D5a", values = c(exposure ="#A94064" , outcome = "#44AA99"))


```

The identified causal relationship between Medicaid expansion and
Medicaid take-up in the revised DAG provides compelling evidence that
changes in the treatment variable directly influence changes in the
outcome variable. This finding suggests that interventions targeting the
treatment variable, such as expanding Medicaid coverage, can potentially
have a substantial impact on improving the rate of Medicaid take-up.

by conducting backdoor analysis I identified the necessary adjustment
set, revealing that variables Citizenship Status, Immigration Policy Climate, Unemployment Rate need to be controlled for to
accurately estimate the causal effect between Medicaid expansion and
Medicaid take-up.

```{r DAG2Adj, echo=FALSE}
adjustmentSets(findag)

```

To enhance the clarity and interpretability of the graph, I employed a
strategy to simplify its complexity. This involved grouping related
variables into single nodes, such as combining 'education,' 'income,'
and 'employment' into a unified node labeled 'Socioeconomic.' The
streamlined representation of the underlying relationships can be
observed in Graph 3.

```{r DAG3, echo=FALSE}


shaddag<-dagitty('dag {
        bb="-3.828,-4.241,3.728,3.459"
        "State Political Ideology" [pos="-3.274,-2.020"]
         Demographics [pos="0.049,-1.978"]
        "Medicaid Expansion" [exposure,pos="-2.803,-0.805"]
        "Immigration Policy Climate" [pos="-2.771,0.180"]
        "Foregin-Born" [pos="-1.294,0.128"]
        "Socioeconomic" [pos="-1.288,-2.010"]
        "Medicaid Take-Up" [outcome,pos="0.049,-0.763"]
        "Unemployment Rate" [pos="-2.478,-2.020"]
        "State Political Ideology" -> "Medicaid Expansion"
        "State Political Ideology" -> "Immigration Policy Climate"
        "State Political Ideology" -> "Unemployment Rate"
        "State Political Ideology" -> "Medicaid Take-Up"
        Demographics -> "Socioeconomic"
        Demographics -> "Medicaid Take-Up"
        "Medicaid Expansion" -> "Medicaid Take-Up"
        "Immigration Policy Climate" -> "Foregin-Born"
        "Immigration Policy Climate" -> "Medicaid Take-Up"
        "Foregin-Born" -> "Socioeconomic"
        "Foregin-Born" <-> "Demographics"
        "Foregin-Born" -> "Medicaid Take-Up"
        "Socioeconomic" -> "Medicaid Take-Up"
        "Unemployment Rate" -> "Medicaid Expansion"
        "Unemployment Rate" -> "Immigration Policy Climate"
        "Unemployment Rate" -> "Socioeconomic"
        "Unemployment Rate" -> "Medicaid Take-Up"
}')

####################
## Create simplified  DAG
####################

DAGSHADI<-ggdag_status(shaddag,node_size = 10,use_labels = "name", text = FALSE)+
        guides(color = FALSE) +  # Turn off legend
        theme_dag()

DAGSHADI$layers[[3]]$mapping <- aes(colour = status)
DAGSHADI + scale_color_manual(na.value ="#222D5a" , values = c(exposure ="#A94064" , outcome = "#44AA99")) +
        scale_fill_manual(na.value ="#222D5a", values = c( exposure ="#A94064" , outcome = "#44AA99")) # other coloer = "#ffc300",  


```

Although utilizing causal discovery algorithms has limitations, such as
assuming the adequacy of observed variables and relying on the absence
of unobserved confounders, efforts were made to include relevant
variables in the analysis. However, it is possible that unmeasured
confounders may exist, potentially introducing biases into the
identified causal relationships. Therefore, the obtained graph may not
precisely represent the true underlying causal structure..

Due to these limitations, I do not solely rely on this graph and its
suggested adjustment set for estimating causal effects in my analysis.
Nonetheless, the DAG derived from the causal discovery approach serves
as a valuable tool for generating hypotheses and guiding the modeling
process, as well as informing the selection of control variables in my
DID approach analysis.

## Descriptive Analysis

> not to include for the original pa

```{r dis1, echo=FALSE}

##weighted:



svy <- as_survey(ACS, weight = PWGTP , repweights = matches("PWGTP[0-9]+"),
                  type = "JK1", scale = 4/ 80 , rscales = rep(1, 80 ), mse = TRUE)

tab<-
  svy %>%
  tbl_strata(
    strata = treat,
    .tbl_fun =
      ~ .x %>% tbl_svysummary(
        by = NATIVITY,
        include = c(SEX, DIS, AGEP,  MARG ,  SCHLG ,  RACE1,  ESRG , POVPIPG),
      )%>%
      add_p()
  )
tab


svy %>%  tbl_svysummary(
    by = expansion,
    include = c(DIS, SEX,  MARG ,SCHLG ,ETHN, ESRG, POVPIPG, RACE,AGEP)
  ) 

## Notweighted

detach("package:dplyr", unload = TRUE)

tbl_1<-
  Data %>%
  select(SEX, DIS, AGEP,  MARG ,  SCHLG ,  RACE1,  ESRG , POVPIPG, NATIVITY, treat,YLIU, PLIU,ENG, GEOR) %>%
  tbl_strata(
    strata = treat,
     .tbl_fun =
      ~ .x %>% tbl_summary(
        by = NATIVITY
      )%>%
      add_p() %>%
add_significance_stars(hide_ci = TRUE, hide_p = FALSE)
  )
tbl_1  

```



Raw data of log homicides per 100,000 for Florida vs never treated
control states.

## Result for event Study and Parallel trend

The main assumption of the Difference-in-Differences (DiD) methodology relies on the presence of parallel trends before the policy implementation.We examine the event-study estimates for uninsured rates and Medicaid take-up to assess the impact of Medicaid expansion on low-income individuals aged 26-64 and assess the validity of parallel trend assumption.


### Event studies for Uninsured rate.  Low-income aged 26-64 

Figure 1 displays the event-study estimates for both unconditional and conditional parallel trends in uninsured rates. In Panel (a), the focus is on the effects of the expansion on uninsured rates for US-born individuals, while Panel (b) examines the effects for foreign-born individuals. The green line with circles in both panels represents the conditional models, while the orange line with triangle represents the unconditional models. For the corresponding estimation coefficients, please refer to Table 1.


As shown in Figure 1, there are no significant pre-trend differences for US-born individuals living in expansion states compared to non-expansion states, as the coefficients are not significantly different from zero. Similarly, for foreign-born individuals, the coefficients for the interaction terms between year and the indicator for the pre-treatment period are also small and not statistically significant, indicating no significant pre-trend differences in the uninsured rates between foreign-born individuals in expansion states and non-expansion states. Moreover, when controlling for characteristics, the coefficients exhibit minimal changes and remain small, further supporting the parallel trend assumption. Additionally, these coefficients do not attain statistical significance, indicating that the characteristics accounted for do not significantly impact the parallel trends assumption.

Transitioning to the post-expansion years, we observe notable and statistically significant declines in the overall uninsured rates for both foreign-born and US-born individuals. The coefficients associated with the indicator variables representing the post-expansion years are negative and demonstrate statistical significance for both groups. These results indicate a clear reduction in uninsured rates following the implementation of Medicaid expansion.

Upon analyzing the results presented in Table 1, it becomes evident that the significance levels of the lag year coefficients tend to be higher for foreign-born individuals compared to US-born individuals. Specifically, in Model 3, the coefficient for the lag year achieves statistical significance at the 5 level for the foreign-born group. In Model 4, it reaches statistical significance at the 0.1 level. In contrast, for the US-born group, the coefficient remains statistically insignificant in both models. These findings suggest stronger evidence of a pre-trend difference in uninsured rates for foreign-born individuals in expansion states compared to non-expansion states, even after accounting for foreign-born specific characteristics. Conversely, the evidence for a pre-trend difference in uninsured rates among US-born individuals is comparatively weaker. The differences in significance levels indicate a potential violation of the parallel trend assumption to a greater extent for foreign-born individuals, implying possible disparities in uninsured rates between expansion and non-expansion states even prior to the implementation of Medicaid expansion.

The event study presented in Figure 1 indicates significant improvements in insurance coverage within the expansion states compared to the non-expansion states following the implementation of Medicaid expansion. However, the observed divergence in uninsured trends and the relatively smaller reduction in the uninsured rate for foreign-born individuals highlight potential disparities in healthcare access. Nevertheless, it is important to note that the gap between the insured rates of foreign-born and US-born individuals started to close after 2018.

```{r fig1, echo=FALSE}

Event1 = feols(UNINS ~ i(ttot, expansion, ref = -1)|                 
                       ST + YEAR,                             ## FEs
               cluster = ~ST,                          ## Clustered SEs
               weights = ~PWGTP,
               data = NATV)

Event2 = feols(UNINS ~ i(ttot, expansion, ref = -1)+.[controls]|                 
                       ST + YEAR,                             ## FEs
               cluster = ~ST,                          ## Clustered SEs
               weights = ~PWGTP,
               data = NATV)

Event3 = feols(UNINS ~ i(ttot, expansion, ref = -1)|                 
                       ST + YEAR,                             ## FEs
               cluster = ~ST,                          ## Clustered SEs
               weights = ~PWGTP,
               data = Forgn)

Event4 = feols(UNINS ~ i(ttot, expansion, ref = -1)+.[controls] + .[foriegn]|                 
                       ST + YEAR,                             ## FEs
               cluster = ~ST,                          ## Clustered SEs
               weights = ~PWGTP,
               data = Forgn)


UNINSUS<-ggiplot(list('wo/ control vars' = Event1, 'with control vars' = Event2),
        ref.line = -1, main = 'US-Born',xlab='Event Time')
#UNINSUS<-UNINSUS+scale_y_continuous(breaks = seq(-0.10, 0.10, by = 0.05))

UNINSFOR<-ggiplot(list('wo/ control vars' = Event3, 'controled' = Event4),
        ref.line = -1, main = 'Foregin-Born',xlab='Event Time')
#UNINSFOR<-UNINSFOR+scale_y_continuous(breaks = seq(-0.15, 0.10, by = 0.05))

figure1<-ggarrange(UNINSUS, UNINSFOR , 
          ncol = 2, nrow = 1)

annotate_figure(figure1,
                top = text_grob("Uninsured Rate", face = "bold", size = 14),
                
                fig.lab = "Figure 1", fig.lab.face = "bold"
                )

```


```{r table1,warning = FALSE,message = FALSE, echo=FALSE}

table1<-etable(list(Event1, Event2, Event3,Event4),
                 digits = 3,
       vcov = "twoway", 
       group = list("^_Controls"=c(controls,foriegn)),
       markdown = TRUE,
      # tex=TRUE,
       depvar=FALSE,
       dict=c("expansion"= "year", "ttot"=""),
        extralines = list("^^Sub-sample" = c("US-Born", "US-Born", "Foreign-Born", "Foreign-Born"))
)

table1

```


#### Event Study for medicaid-take up

Figure 2 and Table 2 present the event-study estimates for the unconditional and conditional parallel trends concerning Medicaid take-up. According to the data presented in Figure 2,prior to the implementation of Medicaid expansion, there is no significant pre-trend difference in Medicaid take-up between expansion and non-expansion states for both low-income US-born and foreign-born individuals aged 26-64. 

For the US-born sub-sample, Model 2 includes control variables, while Model 1 serves as a baseline model. The coefficients for the interaction terms between year and the indicator for the pre-treatment period were generally small and statistically insignificant in both models. This suggests that there is no significant pre-trend difference in uninsured rates between expansion and non-expansion states for US-born individuals.

Similarly, for the foreign-born sub-sample, Model 4 includes control variables, while Model 3 serves as a baseline model. The coefficients for the interaction terms were also small and statistically insignificant in both models, suggesting no significant pre-trend difference in uninsured rates between expansion and non-expansion states for foreign-born individuals.


Furthermore, the coefficients for the interaction terms representing the post-treatment periods (years 0 to 5 after the implementation of Medicaid expansion) were positive and statistically significant in all models, indicating an increase in uninsured rates for both US-born and foreign-born individuals in expansion states compared to non-expansion states during those years.

Analyzing the results presented in Table 2, a notable pattern emerges regarding the Medicaid take-up rates between foreign-born and US-born individuals following the expansion. Initially, during the first three years after the expansion, the Medicaid take-up rate for foreign-born individuals was lower compared to that of US-born individuals. However, a reversal in this observation occurred from year 4 onwards, as the rate of take-up among foreign-born individuals increased.This suggests that over time, foreign-born individuals were able to overcome some of the barriers and obstacles they initially encountered, leading to a higher participation in Medicaid. It is likely that various factors contributed to this trend. Changes in immigration policies, targeted outreach efforts aimed at foreign-born populations, or the implementation of programs specifically designed to enhance healthcare access for immigrants could have played a role in facilitating the increased participation among foreign-born individuals.
Further investigation into the specific policies and initiatives implemented during this period would provide a deeper understanding of the factors influencing the changing Medicaid take-up rates among foreign-born individuals. however, it is surprising to see a higher Medicaid take-up rate for foreign-born individuals during the fourth and fifth years after expansion, which align with the years 2018 and 2019 when stricter immigration policies were implemented under the Trump administration


These findings demonstrate the effectiveness of Medicaid expansion in improving access to healthcare, especially among foreign-born individuals. The absence of significant pre-trend differences and the subsequent increase in Medicaid take-up rates following the expansion highlight the positive impact of the expansion in reducing the uninsured population and promoting healthcare coverage for both US-born and foreign-born individuals in expansion states compared to non-expansion states.


```{r fig2, echo=FALSE}

Event5 = feols(HINS4 ~ i(ttot, expansion, ref = -1)|                 
                       ST + YEAR,                             ## FEs
               cluster = ~ST,                          ## Clustered SEs
               weights = ~PWGTP,
               data = NATV)

Event6 = feols(HINS4 ~ i(ttot, expansion, ref = -1)+.[controls]|                 
                       ST + YEAR,                             ## FEs
               cluster = ~ST,                          ## Clustered SEs
               weights = ~PWGTP,
               data = NATV)


Event7 = feols(HINS4 ~ i(ttot, expansion, ref = -1)|                 
                       ST + YEAR,                             ## FEs
               cluster = ~ST,                          ## Clustered SEs
               weights = ~PWGTP,
               data = Forgn)

Event8 = feols(HINS4 ~ i(ttot, expansion, ref = -1)+.[controls] + .[foriegn]|                 
                       ST + YEAR,                             ## FEs
               cluster = ~ST,                          ## Clustered SEs
               weights = ~PWGTP,
               data = Forgn)


UNINSUS<-ggiplot(list('wo/ control vars' = Event5, 'with control vars' = Event6),
        ref.line = -1, main = 'US-Born',xlab='Event Time')
#UNINSUS<-UNINSUS+scale_y_continuous(breaks = seq(-0.10, 0.10, by = 0.05))


UNINSFOR<-ggiplot(list('wo/ control vars' = Event7, 'controled' = Event8),
        ref.line = -1, main = 'Foregin-Born',xlab='Event Time')
#UNINSFOR<-UNINSFOR+scale_y_continuous(breaks = seq(-0.15, 0.10, by = 0.05))


figure2<-ggarrange(UNINSUS, UNINSFOR , 
          ncol = 2, nrow = 1)

annotate_figure(figure2,
                top = text_grob("Medicaid Takeup Rate", face = "bold", size = 14),
                
                fig.lab = "Figure 2", fig.lab.face = "bold"
                )
```
```{r table 2, warning = FALSE,message = FALSE, echo=FALSE}

table2<-etable(list(Event5, Event6, Event7,Event8),
                 digits = 3,
       vcov = "twoway", 
       group = list("^_Controls"=c(controls,foriegn)),
       markdown = TRUE,
      #tex=TRUE,
       depvar=FALSE,
       dict=c("expansion"= "year", "ttot"=""),
        extralines = list("^^Sub-sample" = c("US-Born", "US-Born", "Foreign-Born", "Foreign-Born"))
)

table2

```
The fixed-effects models accounted for state and year fixed-effects, controlling for unobserved heterogeneity and time-specific factors that could affect uninsured rates. The fit statistics indicate that the models explain a modest proportion of the variation in medicaid take-up, with R-squared values ranging from 0.06514 to 0.18770.

## Difference-in-Differences Model Results



### Weighted OLS

#### Unisured rate
Table 3

```{r table 3, echo=FALSE}

Data$ForeginBorn <- ifelse(Data$NATIVITY == "Foregin-born", 1, 0)

data<-Data
factor_columns <- sapply(data, is.factor)
data[factor_columns] <- lapply(data[factor_columns], as.character)

data <- replace(data, is.na(data), 99999999)

data[factor_columns] <- lapply(data[factor_columns], as.factor)

reg1 = feols(UNINS ~treat*ForeginBorn | ST + YEAR+ sw0(REGION^YEAR) , cluster = ~ST, weights = ~PWGTP, data = data) # state and year fixed effect
reg2 = feols(UNINS ~ treat*ForeginBorn +.[controls]+ ForeginBorn*ENG+ForeginBorn*PLIU + ForeginBorn*IPC | ST + YEAR +REGION^YEAR+ sw0(ST[YEAR]), cluster = ~ST, weights = ~PWGTP, data = data) # state and year fixed effect
reg3 = feols(UNINS ~treat*ForeginBorn+.[adj1]  | ST + YEAR+ sw0(REGION^YEAR) , cluster = ~ST, weights = ~PWGTP, data = data) # state and year fixed effect


table3<-
  etable(list(reg1,reg3,reg2), 
          group = list("^_Controls"=c(controls)),
          digits = 3,
          vcov = "twoway", 
          markdown = TRUE,
          depvar=FALSE,
          dict=c("UnempR"= "state unemployment rate", "ADA"="State Political Ideology"
                 )
)

table3

```
```{r table3a, echo=FALSE}

reg1 = feols(UNINS ~treat*ForeginBorn +.[controls]| ST + YEAR+ sw0(REGION^YEAR) , cluster = ~ST, weights = ~PWGTP, data = data) # state and year fixed effect
reg2 = feols(UNINS ~treat/CIT +.[controls]| ST + YEAR+ sw0(REGION^YEAR) , cluster = ~ST, weights = ~PWGTP, data = data) # state and year fixed effect

Event5 = feols(HINS4 ~ i(ttot, ref = -1)|                 
                       ST + YEAR,                             ## FEs
               cluster = ~ST,                          ## Clustered SEs
               weights = ~PWGTP,
               data = NATV)



etable(reg1,reg2)


```

#### Medicaid Take-up

Table 4 

```{r table 4, echo=FALSE}

```
### Generalized linear model (Logit)

Table 5
```{r table 5, echo=FALSE}

```

Table 6

```{r table 6, echo=FALSE}

```


The results are also robust to using OLS on the outcome levels Given
that for some of the specifications the number of clusters will be less
than 50, I also use the wold-cluster bootstrap approach to inference in
the main regressions

We now turn to estimating the average effect of the laws in a
difference- indifferences regression framework. Results are shown in
Panels A, B, and C of Table 5, which show population- weighted OLS
estimates, unweighted OLS estimates, and estimates from a negative
binomial model. Estimates from the negative binomial regression are
interpreted in the same way as those from a log- linear OLS model.
Results from the population- weighted OLS model shown in Panel A
indicate that

Finally, simulations for the fi xed effect negative binomial model
corresponding to Column 2 in Panel C indicate that 7.6 percent of
placebo estimates are signifi cant at the 5 percent level, while 14.1
percent are signifi cant at the 10 percent level. As shown in Figure 3,
the estimate of 7.3 percent in Table 5 ranks at the 95.7th percentile,
as fewer than 5 percent of placebo estimates were larger than the actual
estimate in the simulations. On the basis of these exercises, we
conclude that it is unlikely that we would have obtained estimates of
the magnitude and statistical signifi cance shown in Panels A, B, and C
of Table 5 due to chance.



## Alternative Specification and Robustness Checks

### TWFE Event studies with control vs (Sun and Abraham, 2020) for whole sample

```{r fig5, echo=FALSE}

df<-Data
# Following Sun and Abraham, we give our never-treated units a fake "treatment"
# date far outside the relevant study period.

df$year_treated <- ifelse(df$expansion == 0, 10000, df$ExpansionY)

# Now we re-run our model from earlier, but this time swapping out 
# `i(time_to_treat, treat, ref = -1)` for `sunab(year_treated, year)`.
# See `?sunab`.

mod_sa = feols(UNINS ~ sunab(year_treated, YEAR) +.[controls] |
                       ST + YEAR,
               cluster = ~ST,
               weights = ~PWGTP,
               data = df)



twfe = feols(UNINS ~ i(ttot, expansion, ref = -1)+.[controls]|                 
                       ST + YEAR,                             ## FEs
               cluster = ~ST,                          ## Clustered SEs
               weights = ~PWGTP,
               data = Data)


UNinPlot<-ggiplot(
        list("TWFE,Event-study" = twfe, "Sun & Abraham (2020)" = mod_sa),
        main = 'Uninsured: Event study: Staggered treatment (TWFE)',
        xlab = 'Time to treatment',
        ref.line = -1
                )


mod_saM = feols(HINS4 ~ sunab(year_treated, YEAR) +.[controls] |
                       ST + YEAR,
               cluster = ~ST,
               weights = ~PWGTP,
               data = df)




twfeM = feols(HINS4 ~ i(ttot, expansion, ref = -1)+.[controls]|                 
                       ST + YEAR,                             ## FEs
               cluster = ~ST,                          ## Clustered SEs
               weights = ~PWGTP,
               data = Data
)



MedicPlot<-ggiplot(
        list("TWFE,Event-study" = twfeM, "Sun & Abraham (2020)" = mod_saM),
        main = 'Medicaid: Event study: Staggered treatment (TWFE) ',
        xlab = 'Time to treatment',
        ref.line = -1
)

ggarrange(MedicPlot, UNinPlot , 
          ncol = 2, nrow = 1)

```

```{r table13, echo=FALSE}

etable(twfeM,mod_saM)

```




Include a table with TWFE and the CS result

## Analyzing Disparities
