---
title: "Notebook for Paper1: Medicaid and FB"
output: html_notebook
---


## 1.Example for Event Study

```{r}

##################################################################################################
git <- haven::read_dta("https://raw.githubusercontent.com/Mixtape-Sessions/Advanced-DID/main/Exercises/Data/ehec_data.dta")

git$treated <- ifelse(is.na(git$yexp2), 0, 1 * (git$year >= git$yexp2))
git$rel_year <- ifelse(is.na(git$yexp2), -100, git$year - git$yexp2)

# Estimate did2s
es_did2s <- did2s(
    git,
    yname = "dins",
    first_stage = ~ 0 | stfips + year,
    second_stage = ~ 0 + i(rel_year, ref = -100),
    treatment = "treated",
    cluster_var = "stfips"
)

###############################################################################################

library(data.table) ## For some minor data wrangling
library(fixest)     ## NB: Requires version >=0.9.0

# Load and prepare data
git2 = fread("https://raw.githubusercontent.com/LOST-STATS/LOST-STATS.github.io/master/Model_Estimation/Data/Event_Study_DiD/bacon_example.csv") 

# Let's create a more user-friendly indicator of which states received treatment
git2[, treat := ifelse(is.na(`_nfd`), 0, 1)]
git2[, time_to_treat := ifelse(treat==1, year - `_nfd`, 0)]


mod_twfe = feols(asmrs ~ i(time_to_treat, treat, ref = -1) + ## Our key interaction: time × treatment status
                     pcinc + asmrh + cases |                    ## Other controls
                     stfips + year,                             ## FEs
                 cluster = ~stfips,                          ## Clustered SEs
                 data = git2)

iplot(mod_twfe, 
      xlab = 'Time to treatment',
      main = 'Event study: Staggered treatment (TWFE)')

###############################################################################################
library(tidyverse); library(fixest)
git3 <- causaldata::organ_donations

# Treatment variable
git3 <- git3 %>% mutate(California = State == 'California')

# Interact quarter with being in the treated group using
# the fixest i() function, which also lets us specify
# a reference perigit3 (using the numeric version of Quarter)
clfe <- feols(Rate ~ i(Quarter_Num, California, ref = 3) | 
                  State + Quarter_Num, data = git3)

# And use coefplot() for a graph of effects
coefplot(clfe)

###############################################################################################


```

## 2. Attempt to Use did2 Package instead of fixest for event study estimation

```{r}
## Creating EVent study

#install.packages("survey")
library(survey)
#install.packages("srvyr")
library("srvyr")
library(did2s) 
install.packages("did2s")

#### subseting 

df <- subset(Data, select=c(ST,YEAR, treat, ttot,expansion, ExpansionY,  Expan_STS, UNINS, NATIVITY))


df$ExpansionY <- ifelse(is.na(df$ExpansionY),10000, df$ExpansionY)
df$ttot <- ifelse(df$ExpansionY==10000, 10000,df$ttot)

df<-df[df$NATIVITY == "Foregin-born", ]


#######################################################################
## Fixest Package

Event = feols(UNINS ~ i(ttot, expansion, ref = c(-1,10000)) |                
                   
                ST + YEAR,                             ## FEs
              #vcov="hetero" ,
              cluster = ~ST ,
              # weights = ~PWGTP,
               data = df)

iplot(Event)



##############################################################

# did2 package

df <- aggregate(. ~ ST+ YEAR, data=df, FUN=mean)


dynamic = did2s(df,
               yname = "UNINS", 
               first_stage = ~ 0 | ST + YEAR,
               second_stage = ~ i(ttot, ref = c(-1,10000)) ,treatment = "treat",
              cluster_var = "ST"
)

iplot(dynamic)



############ Plot both toghther#########

ggiplot(list('dids' = dynamic, 'fixest' = Event),
                 ref.line = -1, main = 'Unadjusted',xlab='Event Time')+
    scale_color_manual(values=c('black','#B64074'))






```

## 3.Create Variables
### 3.1 Create Undocumented variable

```{r}
Data$UNDOC <- 1

# Set UNDOC to 0 based on various conditions:

# The individual is a citizen.
Data$UNDOC[Data$CIT %in% c("Born in US states", "Born in US Territories", "US-citizen Born Abroad", "Naturalized-citizen")] <- 0
# The individual arrived before 1980.
Data$UNDOC[Data$YOEP < 1980] <- 0
# The individual was born in Cuba (as practically all Cuban immigrants were granted refugee status before 2017) 
Data$UNDOC[Data$POBP == 327] <- 0
# The individual is a veteran or is currently in the Armed Forces.
Data$UNDOC[Data$ESR %in% c(4,5) ] <- 0
Data$UNDOC[Data$MIL %in% c(1,2,3) ] <- 0
#e. The individual works in the government sector.
Data$UNDOC[Data$COW %in% c(3,4,5) ] <- 0
# The individual's occupation requires some form of licensing based on borjas (such as physicians, registered nurses, air traffic controllers, and lawyers)
Data$UNDOC[Data$OCCP %in% c (10, 120, 230, 350, 410, 800, 810, 820, 830, 845, 850, 860, 900, 910,
                             930, 940, 2100, 2105, 2145, 2170, 2180, 2205, 2300,
                             2310, 2320, 2330, 2350, 2360, 2400, 2435, 2440, 2545, 2555, 
                             3000, 3010, 3030, 3040, 3050, 3090, 3100, 3110, 3120, 3140,
                             3150, 3160, 3200, 3210, 3220, 3230, 3245, 3250, 3255, 3256, 
                             3258, 3261, 3270, 3300, 3310, 3321, 3322, 3323, 3324, 3330,
                             3401, 3402, 3421, 3422, 3423, 3424, 3430, 3500, 3515, 3520,
                             3545, 3550, 3700, 3710, 3720, 3725, 3740, 3750, 3801, 3802, 
                             3820, 3870, 3910, 3945, 3946, 3946, 6010, 6660, 9030, 9040, 9050, 
                             9121, 9122, 9130, 9141, 9142, 9150, 9210, 9240, 9265, 9300, 9310)] <- 0

# if spouse is citize
# 
# 

Data$good <- ifelse(Data$MAR == 1 & Data$RELP %in% c(21, 23, 1) & Data$UNDOC==0, 1,
                    ifelse(Data$MAR == 1 & Data$RELP %in% c(21, 23, 1) & Data$UNDOC==1, 0,
                           ifelse(Data$MAR == 1 & Data$RELP %in% c(20, 0) & Data$UNDOC==0, 1,
                                  ifelse(Data$MAR == 1 & Data$RELP %in% c(20, 0) & Data$UNDOC==1, 0, 0)
                           )
                    )
)


Data$slegal <- ave(Data$good , Data$YEAR, Data$SERIALNO, FUN = mean)

Data$UNDOC[Data$MAR == 1 & Data$slegal > 0 ] <- 0


```


## 4.Creating Descriptive Table
> Note there is error for lableing expansion in these tables there are reveresed

### 4.1 for all population comparison before treatment 
```{r}
df<-Data

dummy<- subset(df, select=c(RACE1,ESRG,SCHLG ,POVPIPG ))
dummy<-dummy(dummy)
dummy <- dummy %>% mutate_all(as.numeric)
colnm<-colnames(dummy)
colnm<- gsub("RACE1_|SCHLG_|SEX_|ESRG_|POVPIPG_","" ,colnm)
colnm <- gsub("\\.", "", colnm)
colnm
names(dummy)<-colnm
head(dummy)
df <- cbind(dummy, df)


df %>% 
    filter(ACA=="Pre-ACA")%>%
    select(ADA,IPC, UnempR,expansion,UNINS, HINS1,HINS2, HINS4, 
           AGEP, White, Black, Asian, Hispanic, Other, FEMALE,  MARG  ,
           Employed, Unemployed, Notinlaborforce,Lessthanhighschool, Highschool, SomecollegeorAssociatedegree, Collegedegree, Graduateandbeyond,
           Incomebelow100poverty, Income100to138poverty,
           DIS,UNDOC ) %>%
    tbl_summary(
        by = expansion,
        #label = list(ADA ~ "State's Political Liberalism",
        #  UnempR ~"State's Unemployment Rate",
        #  IPC ~ "Immigration Policy Climate", 
        # AGEP ~ "Age", UNINS ~ "Uninsured",
        # HINS4 ~ "Medicaid coverage", SEX ~ "Sex", DIS ~"Disability",
        # ESRG~"Employment status", MARG ~"Married",
        # SCHLG~"Education" , RACE1~"Race/ethnicity",POVPIPG ~ "Federal poverty"),
        statistic = list(all_categorical() ~ "{p}",  all_continuous() ~ "{mean} ({sd})")
    )%>%
    add_difference() %>%
    add_significance_stars(
        pattern= "{estimate}{stars}",
        hide_ci = TRUE,
        hide_p = TRUE
    ) %>%
    modify_table_styling(
        columns = estimate,
        rows = p.value < 0.05,
        text_format = "bold"
    )%>%
    
    # modify_spanning_header(all_stat_cols() ~ "**Table 1.Baseline Comparison of States**") %>%
    modify_header(
        label = "**Variable**",
        stat_1 = '**Expansion**',
        stat_2 = '**Non Expansion**'
    )




```

same table but with weight
```{r}
svy %>% 
    subset(ACA=="Pre-ACA")%>%
    
    tbl_svysummary(
        by = expansion,
        include= c(ADA,IPC, UnempR,expansion,UNINS, HINS1,HINS2, HINS4, 
               AGEP, White, Black, Asian, Hispanic, Other, FEMALE,  MARG  ,
               Employed, Unemployed, Notinlaborforce,Lessthanhighschool, Highschool, SomecollegeorAssociatedegree, Collegedegree, Graduateandbeyond,
               Incomebelow100poverty, Income100to138poverty,
               DIS,UNDOC ),
        
        
        
        #label = list(ADA ~ "State's Political Liberalism",
        #  UnempR ~"State's Unemployment Rate",
        #  IPC ~ "Immigration Policy Climate", 
        # AGEP ~ "Age", UNINS ~ "Uninsured",
        # HINS4 ~ "Medicaid coverage", SEX ~ "Sex", DIS ~"Disability",
        # ESRG~"Employment status", MARG ~"Married",
        # SCHLG~"Education" , RACE1~"Race/ethnicity",POVPIPG ~ "Federal poverty"),
        statistic = list(all_categorical() ~ "{p}",  all_continuous() ~ "{mean} ({sd})")
    )%>%
    add_difference() %>%
    add_significance_stars(
        pattern= "{estimate}{stars}",
        hide_ci = TRUE,
        hide_p = TRUE
    ) %>%
    modify_table_styling(
        columns = estimate,
        rows = p.value < 0.05,
        text_format = "bold"
    )%>%
    
    # modify_spanning_header(all_stat_cols() ~ "**Table 1.Baseline Comparison of States**") %>%
    modify_header(
        label = "**Variable**",
       # stat_1 = '**Expansion**',
        #stat_2 = '**Non Expansion**'
    )


```
 

### 4.2 for native population

```{r}
NATV<-df[df$NATIVITY=="US-born",]


NATV%>% 
    filter(ACA=="Pre-ACA")%>%
    select(ADA,IPC, UnempR,expansion,UNINS, HINS1,HINS2, HINS4, 
           AGEP, White, Black, Asian, Hispanic, Other, FEMALE,  MARG  ,
           Employed, Unemployed, Notinlaborforce,Lessthanhighschool, Highschool, SomecollegeorAssociatedegree, Collegedegree, Graduateandbeyond,
           Incomebelow100poverty, Income100to138poverty,
           DIS,UNDOC ) %>%
    tbl_summary(
        by = expansion,
        #label = list(ADA ~ "State's Political Liberalism",
        #  UnempR ~"State's Unemployment Rate",
        #  IPC ~ "Immigration Policy Climate", 
        # AGEP ~ "Age", UNINS ~ "Uninsured",
        # HINS4 ~ "Medicaid coverage", SEX ~ "Sex", DIS ~"Disability",
        # ESRG~"Employment status", MARG ~"Married",
        # SCHLG~"Education" , RACE1~"Race/ethnicity",POVPIPG ~ "Federal poverty"),
        statistic = list(all_categorical() ~ "{p}",  all_continuous() ~ "{mean} ({sd})")
    )%>%
    add_difference() %>%
    add_significance_stars(
        pattern= "{estimate}{stars}",
        hide_ci = TRUE,
        hide_p = TRUE
    ) %>%
    modify_table_styling(
        columns = estimate,
        rows = p.value < 0.05,
        text_format = "bold"
    ) #%>%
    
    # modify_spanning_header(all_stat_cols() ~ "**Table 1.Baseline Comparison of States**") %>%
   # modify_header(
     #   label = "**Variable**",
     #   stat_1 = '**Expansion**',
      #  stat_2 = '**Non Expansion**'
  #  )


```


### 4.3 for whole foreignborn population

```{r}
Forgn<-Data[Data$NATIVITY=="Foregin-born",]
dummy<- subset(Forgn, select=c(RACE1 ,ESRG,SCHLG ,POVPIPG, CORIGIN, ENG,LTINU ))
dummy<-dummy(dummy)
dummy <- dummy %>% mutate_all(as.numeric)
colnm<-colnames(dummy)
colnm<- gsub("RACE1_|SCHLG_|ESRG_|POVPIPG_|ENG_|CORIGIN_|LTINU_","" ,colnm)
colnm <- gsub("\\.", "", colnm)
colnm <- gsub("\\s+", " ", colnm)
#colnm <- gsub("\\_", "", colnm)
colnm
names(dummy)<-colnm
head(dummy)
Forgn <- cbind(dummy, Forgn)


Forgn %>% 
    filter(ACA=="Pre-ACA")%>%
    select(ADA,IPC, UnempR,expansion,UNINS, HINS1,HINS2, HINS4, 
           AGEP, White, Black, Asian, Hispanic, Other, FEMALE,  MARG  ,
           Employed, Unemployed, Notinlaborforce,Lessthanhighschool, Highschool, SomecollegeorAssociatedegree, Collegedegree, Graduateandbeyond,
           Incomebelow100poverty, Income100to138poverty,
           DIS,UNDOC,EasternAsia, EasternEurope, LatinAmerica, MiddleEast, NorthernAmeric,
           OceaniaandatSea, SouthCenteralAsia, SoutheaasternAsia, SubSaharanAfrica,
           UnitedStates, WesternEurope,
           Onlyenglish, Verywell, Well, Notwell, Notatall  ) %>%
    tbl_summary(
        by = expansion,
        #label = list(ADA ~ "State's Political Liberalism",
        #  UnempR ~"State's Unemployment Rate",
        #  IPC ~ "Immigration Policy Climate", 
        # AGEP ~ "Age", UNINS ~ "Uninsured",
        # HINS4 ~ "Medicaid coverage", SEX ~ "Sex", DIS ~"Disability",
        # ESRG~"Employment status", MARG ~"Married",
        # SCHLG~"Education" , RACE1~"Race/ethnicity",POVPIPG ~ "Federal poverty"),
        statistic = list(all_categorical() ~ "{p}",  all_continuous() ~ "{mean} ({sd})")
    )%>%
    add_difference() %>%
    add_significance_stars(
        pattern= "{estimate}{stars}",
        hide_ci = TRUE,
        hide_p = TRUE
    ) %>%
    modify_table_styling(
        columns = estimate,
        rows = p.value < 0.05,
        text_format = "bold"
    )%>%
    
    # modify_spanning_header(all_stat_cols() ~ "**Table 1.Baseline Comparison of States**") %>%
    modify_header(
        label = "**Variable**",
        stat_1 = '**Expansion**',
        stat_2 = '**Non Expansion**'
    )



```

####4.3.1 For Foreign-born citizen

```{r}

# NOW I want to take a look at the pre-trend for Naturalized Citizen

NATCIT<-Forgn[Forgn$CIT=="Naturalized-citizen",]


#NOW the pretrend table for NATCIT
NATCIT %>% 
    filter(ACA=="Pre-ACA")%>%
    select(ADA,IPC, UnempR,expansion,UNINS, HINS1,HINS2, HINS4, 
           AGEP, White, Black, Asian, Hispanic, Other, FEMALE,  MARG  ,
           Employed, Unemployed, Notinlaborforce,Lessthanhighschool, Highschool, SomecollegeorAssociatedegree, Collegedegree, Graduateandbeyond,
           Incomebelow100poverty, Income100to138poverty,
           DIS,EasternAsia, EasternEurope, LatinAmerica, MiddleEast, NorthernAmeric,
           OceaniaandatSea, SouthCenteralAsia, SoutheaasternAsia, SubSaharanAfrica,
            WesternEurope,
           Onlyenglish, Verywell, Well, Notwell, Notatall  ) %>%
    tbl_summary(
        by = expansion,
        #label = list(ADA ~ "State's Political Liberalism",
        #  UnempR ~"State's Unemployment Rate",
        #  IPC ~ "Immigration Policy Climate", 
        # AGEP ~ "Age", UNINS ~ "Uninsured",
        # HINS4 ~ "Medicaid coverage", SEX ~ "Sex", DIS ~"Disability",
        # ESRG~"Employment status", MARG ~"Married",
        # SCHLG~"Education" , RACE1~"Race/ethnicity",POVPIPG ~ "Federal poverty"),
        statistic = list(all_categorical() ~ "{p}",  all_continuous() ~ "{mean} ({sd})")
    )%>%
    add_difference() %>%
    add_significance_stars(
        pattern= "{estimate}{stars}",
        hide_ci = TRUE,
        hide_p = TRUE
    ) %>%
    modify_table_styling(
        columns = estimate,
        rows = p.value < 0.05,
        text_format = "bold"
    )%>%
    
    # modify_spanning_header(all_stat_cols() ~ "**Table 1.Baseline Comparison of States**") %>%
    modify_header(
        label = "**Variable**",
        stat_1 = '**Expansion**',
        stat_2 = '**Non Expansion**'
    )



```

####4.3.2 For Foreign-born Non-Citizen

```{r}
NONCIT<-Forgn[Forgn$CIT=="Non-citizen",]

NONCIT %>% 
    filter(ACA=="Pre-ACA")%>%
    select(ADA,IPC, UnempR,expansion,UNINS, HINS1,HINS2, HINS4, 
           AGEP, White, Black, Asian, Hispanic, Other, FEMALE,  MARG  ,
           Employed, Unemployed, Notinlaborforce,Lessthanhighschool, Highschool, SomecollegeorAssociatedegree, Collegedegree, Graduateandbeyond,
           Incomebelow100poverty, Income100to138poverty,
           DIS,UNDOC,EasternAsia, EasternEurope, LatinAmerica, MiddleEast, NorthernAmeric,
           OceaniaandatSea, SouthCenteralAsia, SoutheaasternAsia, SubSaharanAfrica,
           UnitedStates, WesternEurope,
           Onlyenglish, Verywell, Well, Notwell, Notatall  ) %>%
    tbl_summary(
        by = expansion,
        #label = list(ADA ~ "State's Political Liberalism",
                   #  UnempR ~"State's Unemployment Rate",
                   #  IPC ~ "Immigration Policy Climate", 
                    # AGEP ~ "Age", UNINS ~ "Uninsured",
                    # HINS4 ~ "Medicaid coverage", SEX ~ "Sex", DIS ~"Disability",
                    # ESRG~"Employment status", MARG ~"Married",
                    # SCHLG~"Education" , RACE1~"Race/ethnicity",POVPIPG ~ "Federal poverty"),
        statistic = list(all_categorical() ~ "{p}",  all_continuous() ~ "{mean} ({sd})")
    )%>%
    add_difference() %>%
    add_significance_stars(
        pattern= "{estimate}{stars}",
        hide_ci = TRUE,
        hide_p = TRUE
    ) %>%
    modify_table_styling(
        columns = estimate,
        rows = p.value < 0.05,
        text_format = "bold"
    )%>%
    
    # modify_spanning_header(all_stat_cols() ~ "**Table 1.Baseline Comparison of States**") %>%
    modify_header(
        label = "**Variable**",
        stat_1 = '**Expansion**',
        stat_2 = '**Non Expansion**'
    )

```



##### 4.3.2.1 Foreign-born Non-Citizen Undocumented

```{r}

UNDOCFB<-NONCIT[NONCIT$UNDOC==1,]


#NOW the pretrend table for NATCIT
UNDOCFB %>% 
    filter(ACA=="Pre-ACA")%>%
    select(ADA,IPC, UnempR,expansion,UNINS, HINS1,HINS2, HINS4, 
           AGEP, White, Black, Asian, Hispanic, Other, FEMALE,  MARG  ,
           Employed, Unemployed, Notinlaborforce,Lessthanhighschool, Highschool, SomecollegeorAssociatedegree, Collegedegree, Graduateandbeyond,
           Incomebelow100poverty, Income100to138poverty,
           DIS,EasternAsia, EasternEurope, LatinAmerica, MiddleEast, NorthernAmeric,
           OceaniaandatSea, SouthCenteralAsia, SoutheaasternAsia, SubSaharanAfrica,
           WesternEurope,
           Onlyenglish, Verywell, Well, Notwell, Notatall  ) %>%
    tbl_summary(
        by = expansion,
        #label = list(ADA ~ "State's Political Liberalism",
        #  UnempR ~"State's Unemployment Rate",
        #  IPC ~ "Immigration Policy Climate", 
        # AGEP ~ "Age", UNINS ~ "Uninsured",
        # HINS4 ~ "Medicaid coverage", SEX ~ "Sex", DIS ~"Disability",
        # ESRG~"Employment status", MARG ~"Married",
        # SCHLG~"Education" , RACE1~"Race/ethnicity",POVPIPG ~ "Federal poverty"),
        statistic = list(all_categorical() ~ "{p}",  all_continuous() ~ "{mean} ({sd})")
    )%>%
    add_difference() %>%
    add_significance_stars(
        pattern= "{estimate}{stars}",
        hide_ci = TRUE,
        hide_p = TRUE
    ) %>%
    modify_table_styling(
        columns = estimate,
        rows = p.value < 0.05,
        text_format = "bold"
    )%>%
    
    # modify_spanning_header(all_stat_cols() ~ "**Table 1.Baseline Comparison of States**") %>%
    modify_header(
        label = "**Variable**",
        stat_1 = '**Expansion**',
        stat_2 = '**Non Expansion**'
    )



```


##### 4.3.2.2 Foreign-born Non-Citizen Hispanic

```{r}

NONCITHISP<-NONCIT[NONCIT$Hispanic==1,]


#NOW the pretrend table for NATCIT
NONCITHISP %>% 
    filter(ACA=="Pre-ACA")%>%
    select(ADA,IPC, UnempR,expansion,UNINS, HINS1,HINS2, HINS4, 
           AGEP, White, Black, Asian, Hispanic, Other, FEMALE,  MARG  ,
           Employed, Unemployed, Notinlaborforce,Lessthanhighschool, Highschool, SomecollegeorAssociatedegree, Collegedegree, Graduateandbeyond,
           Incomebelow100poverty, Income100to138poverty,
           DIS,EasternAsia, EasternEurope, LatinAmerica, MiddleEast, NorthernAmeric,
           OceaniaandatSea, SouthCenteralAsia, SoutheaasternAsia, SubSaharanAfrica,
           WesternEurope,
           Onlyenglish, Verywell, Well, Notwell, Notatall  ) %>%
    tbl_summary(
        by = expansion,
        #label = list(ADA ~ "State's Political Liberalism",
        #  UnempR ~"State's Unemployment Rate",
        #  IPC ~ "Immigration Policy Climate", 
        # AGEP ~ "Age", UNINS ~ "Uninsured",
        # HINS4 ~ "Medicaid coverage", SEX ~ "Sex", DIS ~"Disability",
        # ESRG~"Employment status", MARG ~"Married",
        # SCHLG~"Education" , RACE1~"Race/ethnicity",POVPIPG ~ "Federal poverty"),
        statistic = list(all_categorical() ~ "{p}",  all_continuous() ~ "{mean} ({sd})")
    )%>%
    add_difference() %>%
    add_significance_stars(
        pattern= "{estimate}{stars}",
        hide_ci = TRUE,
        hide_p = TRUE
    ) %>%
    modify_table_styling(
        columns = estimate,
        rows = p.value < 0.05,
        text_format = "bold"
    )%>%
    
    # modify_spanning_header(all_stat_cols() ~ "**Table 1.Baseline Comparison of States**") %>%
    modify_header(
        label = "**Variable**",
        stat_1 = '**Expansion**',
        stat_2 = '**Non Expansion**'
    )

```

