---
title: "R Notebook"
output: html_notebook
---

## Event study
For event study to see how the effect of the expansion differ between two groups I did it in two different ways.

1. Running the equation 1 on two sample of Foreign and Native



2. Use the interaction term for Foreign-born following the equation 2

 problem with using the second method is that the power of the analysis might reduce dramaticly. Maybe I can do the power analysis instead of checking all these 
 
 
 I want to see how these two approach differ here is how
 
 when I use no adjustment 
 
### Event study table  no adjustment Check different specifications

```{r}

# with no adjustment on two samples
Event= feols( UNINS ~ i(ttot, expansion, ref = -1) | 
                   ST + YEAR   ,                        ## FEs
               vcov="hetero",
               #  cluster = "ST",
               weights = ~PWGTP,
               data = Data,
               split= ~NATIVITY)
# with no adjustment with interaction 

Event1= feols( UNINS ~ ForeginBorn*i(ttot, expansion, ref = -1) | 
                ST + YEAR   ,                        ## FEs
              vcov="hetero",
              #  cluster = "ST",
              weights = ~PWGTP,
              data = Data)

etable(Event, Event1)



```
Plotting the same thing in a graph:

### Graph Event study   no adjustment

```{r, echo=FALSE}

# with no adjustment on two samples

plot1<-ggiplot(Event)


# with no adjustment with interaction 
treatment_var<- c("ForeginBorn")
plotleglable<- c('US-Born','Foregin-born')



draft<-coeftable(Event1) 
draft<-as.data.frame(draft)
    
    existing_rows <- variable_list[variable_list %in% rownames(draft)]
    
    if (length(existing_rows) > 0) {
        dropOutFtab <- which(rownames(draft) %in% existing_rows)
        draft <- draft[-dropOutFtab, ]
    }
    
    #grep("ttot",rownames(draft)))
    checkmark<-any(grepl(treatment_var,rownames(draft)))    
    if (checkmark) {
        plot<-draft[1:(nrow(draft)/2),1:2] 
    } else {
        plot<-draft[,1:2]   
    }
    
    plot$id<-1
    plot$x_year<-as.numeric(gsub("[^0-9.-]", "", rownames(plot))) # extracting year variable from row names
    colnams<-c("estimate","sd","id", "x_year") #assigning names
    colnames(plot)<- colnams
    ############## Calculating the est of interaction #############
    #
    est1<-draft[1:(nrow(draft)/2),1]
    est2<-draft[((nrow(draft)/2)+1):nrow(draft),1]
    est3<-est2+est1
    
    ############## # Calculate standard error for each pair of rows and columns#############
    
    cov<-vcov(Event1, "hetero")
    
    if (length(existing_rows) > 0) {
        dropOutFtab <- which(rownames(cov) %in% existing_rows)
        cov<-cov[-dropOutFtab,-dropOutFtab]
    }
    
    #se_treat_male <- sqrt(cov[1, 1] + cov[2, 2] + 2 * cov[1, 2]) ->
    if (checkmark) { 
        i <- 1    
        j <- nrow(cov)/2
        se_list <-list()  # numeric(nrow(cov)/2) ## initiating a vector for calculating SE for the desired plot
        while (i <= j) {
            #for (i in 1:row(cov)/2) {
            se_list[[i]] <- sqrt(cov[i, i] + cov[i+j, i+j] + 2 * cov[i, i+j])
            i <- i + 1
        }
        
        cosd<-data.frame(se = unlist(se_list))
        cosd<-data.frame(estimate= est3)
        cosd$se<-unlist(se_list)
        cosd$id<-2
        cosd$x_year<-as.numeric(gsub("[^0-9.-]", "", rownames(plot)))
        
        colnames(cosd)<- colnams
        
        plot<-rbind(plot,cosd)
        
    }
    
    
    ############## Calculating the est of interaction #############
    
    plot$prms.ci_low<- plot$estimate - qnorm(0.975) * plot$sd
    plot$prms.ci_high<- plot$estimate + qnorm(0.975) * plot$sd
    
    
    
    #plot$ci_treat_male <- est1 + c(-1,1) * qnorm(0.975) * 0.001735147
    
    
    #############################Prepare the table for ploting ################################## 
    
    plot$label<-plot$x_year
    nrplot<-nrow(plot)
    plot$x_year<-ifelse(1:nrplot < nrplot/2 , plot$x_year-0.1, plot$x_year+0.1)

plot2<-ggplot(plot,
                 aes(
                     x =x_year, y =estimate,group =as.factor(id),
                     ymin = prms.ci_low , ymax = prms.ci_high ,col=as.factor(id)
                 ))+
        labs(title = "Effec on UNINS", x="Time to Treatment", y="Estimate and 95% Conf. Int")+
        geom_hline(yintercept = 0)+
        geom_point(aes(shape=as.factor(id)),size=3) +
        geom_errorbar(width = 0.07) +
        geom_vline(xintercept = -1, lty =  "dashed")+
        # geom_ribbon(alpha = 0.2) +
        #labs(title = "Your Title", x = "X-axis Label", y = "Y-axis Label") +
        scale_colour_manual(labels=plotleglable,name="Population",values=cbPalette)+
        scale_shape_discrete(labels=plotleglable,name="Population")+
        scale_y_continuous(breaks = scales::breaks_pretty()) +
        theme(panel.background = element_rect(fill = "white", colour = "grey50"),legend.position="bottom", plot.title = element_text(hjust = 0.5))
         #  geom_styl


ggarrange(plot1, plot2, ncol = 2, nrow = 1)


```






Now I wannt see if I use the same set of covariate for both regression or use different for each what would be the difference

### Checking how adjustment affect estimate on splited result 
```{r}

# with adjustment on two samples
Event= feols( UNINS ~ i(ttot, expansion, ref = -1)+ SEX+DIS+AGEP+SCHLG+POVPIPG+MARG+RACE1+ESRG+ ENG+LTINU+NonCit+ADA+UnempR+IPC | 
                   ST + YEAR   ,                        ## FEs
               vcov="hetero",
               #  cluster = "ST",
               weights = ~PWGTP,
               data = Data,
               split= ~NATIVITY)


Event1= feols( UNINS ~ i(ttot, expansion, ref = -1)+ SEX+DIS+AGEP+SCHLG+POVPIPG+MARG+RACE1+ESRG+ADA+UnempR  | 
                   ST + YEAR   ,                        ## FEs
               vcov="hetero",
               #  cluster = "ST",
               weights = ~PWGTP,
               data = NATV)


Event2= feols( UNINS ~ i(ttot, expansion, ref = -1)+ SEX+DIS+AGEP+SCHLG+POVPIPG+MARG+RACE1+ESRG+ENG+LTINU+NonCit+ADA+UnempR+IPC | 
                   ST + YEAR   ,                        ## FEs
               vcov="hetero",
               #  cluster = "ST",
               weights = ~PWGTP,
               data = Forgn
               )
etable(Event,Event1,Event2)

```
 
 While it might have influnce the power it didn't affect the estimation so, I will keep using the split version with all control now checkin how it would differ if I include adjustment
 
### Event study table with adjustment Check different specifications

```{r}
# with adjustment on two samples including IPC & NonCit
# 

Event= feols( UNINS ~ i(ttot, expansion, ref = -1) +
               SEX+DIS+AGEP+SCHLG+POVPIPG+MARG+RACE1+ESRG+ENG+LTINU+NonCit+ADA+UnempR+IPC | 
                   ST + YEAR   ,                        ## FEs
               vcov="hetero",
               #  cluster = "ST",
               weights = ~PWGTP,
               data = Data,
               split= ~NATIVITY)

Event1= feols( UNINS ~ ForeginBorn*i(ttot, expansion, ref = -1)+
               SEX+DIS+AGEP+SCHLG+POVPIPG+MARG+RACE1+ESRG+ENG+LTINU+NonCit+ADA+UnempR+IPC | 
                   ST + YEAR   ,                        ## FEs
               vcov="hetero",
               #  cluster = "ST",
               weights = ~PWGTP,
               data = Data)

Event2= feols( UNINS ~ ForeginBorn*i(ttot, expansion, ref = -1) 
               + SEX + DIS+AGEP+POVPIPG+ENG+LTINU+NonCit+ForeginBorn*(SCHLG+ MARG+ RACE1 + ESRG + ADA+UnempR+IPC) | 
                ST + YEAR   ,                        ## FEs
              vcov="hetero",
              #  cluster = "ST",
              weights = ~PWGTP,
              data = Data)




etable(Event,Event1,Event2)
```




 
### plot all adj Event study splited and non splited
 
```{r,  fig.height = 8, fig.width = 9 , echo=FALSE}
plot1<-ggiplot(Event)



### for interaction including IPC and NonCit

controlvar<-c("UnempR","SEX","DIS", "AGEP","SCHLG", "MARG", "RACE1", "ESRG","ENG", "LTINU","NonCit", "IPC","POVPIPG","ADA") 
variable_list<- c("ForeginBorn"   , "UnempR" , "SEX"   ,  "DIS"   ,  "AGEP"    ,"SCHLG.L", "SCHLG.Q" ,"SCHLG.C", "SCHLG^4", "MARG",
                  "ESRG.L" , "ESRG.Q",  "ENG.L" ,  "ENG.Q"  , "RACE1.L", "RACE1.Q", "RACE1.C", "RACE1^4",
                   "ENG.C" ,  "ENG^4" ,  "LTINU" , "NonCit", "IPC", "POVPIPG.L","ADA")
treatment_var<- c("ForeginBorn")
plotleglable<- c('US-Born','Foregin-born')



  draft<-coeftable(Event1) 
  draft<-as.data.frame(draft)
  
  existing_rows <- variable_list[variable_list %in% rownames(draft)]
  
  if (length(existing_rows) > 0) {
    dropOutFtab <- which(rownames(draft) %in% existing_rows)
    draft <- draft[-dropOutFtab, ]
  }
  
  #grep("ttot",rownames(draft)))
  checkmark<-any(grepl(treatment_var,rownames(draft)))    
  if (checkmark) {
    plot<-draft[1:(nrow(draft)/2),1:2] 
  } else {
    plot<-draft[,1:2]   
  }
  
  plot$id<-1
  plot$x_year<-as.numeric(gsub("[^0-9.-]", "", rownames(plot))) # extracting year variable from row names
  colnams<-c("estimate","sd","id", "x_year") #assigning names
  colnames(plot)<- colnams
  ############## Calculating the est of interaction #############
  #
  est1<-draft[1:(nrow(draft)/2),1]
  est2<-draft[((nrow(draft)/2)+1):nrow(draft),1]
  est3<-est2+est1
  
  ############## # Calculate standard error for each pair of rows and columns#############
  
  cov<-vcov(Event1, "hetero")
  
  if (length(existing_rows) > 0) {
    dropOutFtab <- which(rownames(cov) %in% existing_rows)
    cov<-cov[-dropOutFtab,-dropOutFtab]
  }
  
  #se_treat_male <- sqrt(cov[1, 1] + cov[2, 2] + 2 * cov[1, 2]) ->
  if (checkmark) { 
    i <- 1    
    j <- nrow(cov)/2
    se_list <-list()  # numeric(nrow(cov)/2) ## initiating a vector for calculating SE for the desired plot
    while (i <= j) {
      #for (i in 1:row(cov)/2) {
      se_list[[i]] <- sqrt(cov[i, i] + cov[i+j, i+j] + 2 * cov[i, i+j])
      i <- i + 1
    }
    
    cosd<-data.frame(se = unlist(se_list))
    cosd<-data.frame(estimate= est3)
    cosd$se<-unlist(se_list)
    cosd$id<-2
    cosd$x_year<-as.numeric(gsub("[^0-9.-]", "", rownames(plot)))
    
    colnames(cosd)<- colnams
    
    plot<-rbind(plot,cosd)
    
  }
  
 
  ############## Calculating the est of interaction #############
  
  plot$prms.ci_low<- plot$estimate - qnorm(0.975) * plot$sd
  plot$prms.ci_high<- plot$estimate + qnorm(0.975) * plot$sd
  
  
  
  #plot$ci_treat_male <- est1 + c(-1,1) * qnorm(0.975) * 0.001735147
  
  
  #############################Prepare the table for ploting ################################## 
  
  plot$label<-plot$x_year
  nrplot<-nrow(plot)
  plot$x_year<-ifelse(1:nrplot < nrplot/2 , plot$x_year-0.1, plot$x_year+0.1)
  
  
plot2<-ggplot(plot,
                 aes(
                     x =x_year, y =estimate,group =as.factor(id),
                     ymin = prms.ci_low , ymax = prms.ci_high ,col=as.factor(id)
                 ))+
        labs(title = "Effec on UNINS", x="Time to Treatment", y="Estimate and 95% Conf. Int")+
        geom_hline(yintercept = 0)+
        geom_point(aes(shape=as.factor(id)),size=3) +
        geom_errorbar(width = 0.07) +
        geom_vline(xintercept = -1, lty =  "dashed")+
        # geom_ribbon(alpha = 0.2) +
        #labs(title = "Your Title", x = "X-axis Label", y = "Y-axis Label") +
        scale_colour_manual(labels=plotleglable,name="Population",values=cbPalette)+
        scale_shape_discrete(labels=plotleglable,name="Population")+
        scale_y_continuous(breaks = scales::breaks_pretty()) +
        theme(panel.background = element_rect(fill = "white", colour = "grey50"),legend.position="bottom", plot.title = element_text(hjust = 0.5))
         #  geom_styl





### Plot 3


controlvar<-c("UnempR","SEX","DIS", "AGEP","SCHLG", "MARG", "RACE1", "ESRG","ENG", "LTINU","NonCit", "IPC","POVPIPG","ADA") 
variable_list<- c("ForeginBorn"   , "UnempR" , "SEX"   ,  "DIS"   ,  "AGEP"    ,"SCHLG.L", "SCHLG.Q" ,"SCHLG.C", "SCHLG^4", "MARG",
                  "ESRG.L" , "ESRG.Q",  "ENG.L" ,  "ENG.Q"  , "RACE1.L", "RACE1.Q", "RACE1.C", "RACE1^4",
                   "ENG.C" ,  "ENG^4" ,  "LTINU" , "NonCit", "IPC", "POVPIPG.L", "ForeginBorn:LTINU", "ForeginBorn:RACE1.L", "ForeginBorn:RACE1.Q", "ForeginBorn:RACE1.C", "ForeginBorn:RACE1^4", "ForeginBorn:SCHLG.L", "ForeginBorn:SCHLG.Q" ,"ForeginBorn:SCHLG.C", "ForeginBorn:SCHLG^4", 'ForeginBorn:MARG', "ForeginBorn:IPC", "ForeginBorn:ESRG.L" , "ForeginBorn:ESRG.Q","ADA","ForeginBorn:ADA","ForeginBorn:UnempR" )
treatment_var<- c("ForeginBorn")
plotleglable<- c('US-Born','Foregin-born')




  draft<-coeftable(Event2) 
  draft<-as.data.frame(draft)
  
  existing_rows <- variable_list[variable_list %in% rownames(draft)]
  
  if (length(existing_rows) > 0) {
    dropOutFtab <- which(rownames(draft) %in% existing_rows)
    draft <- draft[-dropOutFtab, ]
  }
  
  #grep("ttot",rownames(draft)))
  checkmark<-any(grepl(treatment_var,rownames(draft)))    
  if (checkmark) {
    plot<-draft[1:(nrow(draft)/2),1:2] 
  } else {
    plot<-draft[,1:2]   
  }
  
  plot$id<-1
  plot$x_year<-as.numeric(gsub("[^0-9.-]", "", rownames(plot))) # extracting year variable from row names
  colnams<-c("estimate","sd","id", "x_year") #assigning names
  colnames(plot)<- colnams
  ############## Calculating the est of interaction #############
  #
  est1<-draft[1:(nrow(draft)/2),1]
  est2<-draft[((nrow(draft)/2)+1):nrow(draft),1]
  est3<-est2+est1
  
  ############## # Calculate standard error for each pair of rows and columns#############
  
  cov<-vcov(Event2, "hetero")
  
  if (length(existing_rows) > 0) {
    dropOutFtab <- which(rownames(cov) %in% existing_rows)
    cov<-cov[-dropOutFtab,-dropOutFtab]
  }
  
  #se_treat_male <- sqrt(cov[1, 1] + cov[2, 2] + 2 * cov[1, 2]) ->
  if (checkmark) { 
    i <- 1    
    j <- nrow(cov)/2
    se_list <-list()  # numeric(nrow(cov)/2) ## initiating a vector for calculating SE for the desired plot
    while (i <= j) {
      #for (i in 1:row(cov)/2) {
      se_list[[i]] <- sqrt(cov[i, i] + cov[i+j, i+j] + 2 * cov[i, i+j])
      i <- i + 1
    }
    
    cosd<-data.frame(se = unlist(se_list))
    cosd<-data.frame(estimate= est3)
    cosd$se<-unlist(se_list)
    cosd$id<-2
    cosd$x_year<-as.numeric(gsub("[^0-9.-]", "", rownames(plot)))
    
    colnames(cosd)<- colnams
    
    plot<-rbind(plot,cosd)
    
  }
  
  
  ############## Calculating the est of interaction #############
  
  plot$prms.ci_low<- plot$estimate - qnorm(0.975) * plot$sd
  plot$prms.ci_high<- plot$estimate + qnorm(0.975) * plot$sd
  
  
  
  #plot$ci_treat_male <- est1 + c(-1,1) * qnorm(0.975) * 0.001735147
  
  
  #############################Prepare the table for ploting ################################## 
  
  plot$label<-plot$x_year
  nrplot<-nrow(plot)
  plot$x_year<-ifelse(1:nrplot < nrplot/2 , plot$x_year-0.1, plot$x_year+0.1)
  
  
plot3<-ggplot(plot,
                 aes(
                     x =x_year, y =estimate,group =as.factor(id),
                     ymin = prms.ci_low , ymax = prms.ci_high ,col=as.factor(id)
                 ))+
        labs(title = "Effec on UNINS", x="Time to Treatment", y="Estimate and 95% Conf. Int")+
        geom_hline(yintercept = 0)+
        geom_point(aes(shape=as.factor(id)),size=3) +
        geom_errorbar(width = 0.07) +
        geom_vline(xintercept = -1, lty =  "dashed")+
        # geom_ribbon(alpha = 0.2) +
        #labs(title = "Your Title", x = "X-axis Label", y = "Y-axis Label") +
        scale_colour_manual(labels=plotleglable,name="Population",values=cbPalette)+
        scale_shape_discrete(labels=plotleglable,name="Population")+
        scale_y_continuous(breaks = scales::breaks_pretty()) +
        theme(panel.background = element_rect(fill = "white", colour = "grey50"),legend.position="bottom", plot.title = element_text(hjust = 0.5))
         #  geom_styl



ggarrange(plot1, plot2,plot3)


```
 
 given that removing IPC and NonCit didn't affact the result in neither of example I will keep these in model. I want to also run another event study that interaction for Foreignborn and IPC . I suspect to see that it become more like the DID. but let's see
 
## Static TWFE
 Now I started feeling that maybe if I take a look at the samples in the TWFE model two samples then I can chose between model two and three as well.
 
 let's see:
 
 
### TWFE with not adjustment

```{r}


reg1 = feols(UNINS ~ treat  | ST + YEAR  , vcov = "hetero", weights = ~PWGTP, data = Data,split= ~NATIVITY) # Control for demographic + immigrants + state

reg2 = feols(UNINS ~ treat*ForeginBorn  | ST + YEAR  , vcov = "hetero", weights = ~PWGTP, data = Data) # Control for demographic + immigrants + state


etable(list(reg1,reg2))


```


## Run the Sun&Abraham

```{r}


Data$year_treated <- ifelse(Data$expansion == 0, 10000, Data$ExpansionY)



san= feols( UNINS ~ sunab(year_treated, YEAR) +
               SEX+DIS+AGEP+SCHLG+POVPIPG+MARG+RACE1+ESRG+ENG+LTINU+NonCit+ADA+UnempR+IPC | 
                ST + YEAR   ,                        ## FEs
               vcov="hetero",
               #  cluster = "ST",
               weights = ~PWGTP,
               data = Data,
               split= ~NATIVITY)

San1= feols( UNINS ~ ForeginBorn*sunab(year_treated, YEAR)+
               SEX+DIS+AGEP+SCHLG+POVPIPG+MARG+RACE1+ESRG+ENG+LTINU+NonCit+ADA+UnempR+IPC | 
                   ST + YEAR   ,                        ## FEs
               vcov="hetero",
               #  cluster = "ST",
               weights = ~PWGTP,
               data = Data)

San2= feols( UNINS ~ ForeginBorn sunab(year_treated, YEAR) 
               + SEX + DIS+AGEP+POVPIPG+ENG+LTINU+NonCit+ForeginBorn*(SCHLG+ MARG+ RACE1 + ESRG + ADA+UnempR+IPC) | 
                ST + YEAR   ,                        ## FEs
              vcov="hetero",
              #  cluster = "ST",
              weights = ~PWGTP,
              data = Data)

etable(san,San1,San2)

```



### TWFE with adjustment


```{r}

reg1 = feols(UNINS ~ treat + SEX+DIS+AGEP+SCHLG+POVPIPG+MARG+RACE1+ESRG+ENG+LTINU+NonCit+ADA+UnempR+IPC | ST + YEAR  , vcov = "hetero", weights = ~PWGTP, data = Data,split= ~NATIVITY) # Control for demographic + immigrants + state

reg2=  feols(UNINS ~ treat*ForeginBorn + SEX + DIS+AGEP+POVPIPG+ENG+LTINU+NonCit+ForeginBorn*(SCHLG+ MARG+ RACE1 + ESRG + ADA+UnempR+IPC)  | ST + YEAR , vcov = "hetero", weights = ~PWGTP, data = Data)

reg3=  feols(UNINS ~ treat*ForeginBorn +SEX+DIS+AGEP+SCHLG+POVPIPG+MARG+RACE1+ESRG+ENG+LTINU+NonCit+ADA+UnempR+IPC  | ST + YEAR , vcov = "hetero", weights = ~PWGTP, data = Data)


etable(list(reg1,reg2,reg3),fitstat=c('n', 'cor2', 'ar2', 'war2',"aic"))
```
 
 
 checking different specification strategy again
```{r}

Event= feols( UNINS ~ ForeginBorn*i(ttot, expansion, ref = -1) + SEX +DIS+AGEP+POVPIPG+ADA+LTINU+ ForeginBorn*(SCHLG+ MARG+ RACE1 + ESRG+ UnempR+IPC)| 
                ST + YEAR  ,                        ## FEs
              vcov="hetero",
              #  cluster = "ST",
              weights = ~PWGTP,
              data = Data)


```
 
 
 